### 2018-04-04 DraftTeachingAlgorithmicGameTheorywithProgram.tex
Draft TeX

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\date{}

\begin{document}

{Teaching Algorithmic Game Theory with Programming Competitions}

{Andrew Wonnacott}

{COS 398 IW 09 (Professor Walker)}

\begin{itemize}
\tightlist
\item
  {Abstract}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Framing: Developing A Modular Framework for Developing, Deploying,
  and Evaluating programming Assignments in a theory course}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Introduction 1.5}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {goal}{~(1st par) - helping improve the quality of theory eduction for
  broader cs majors - what will I contribute?}
\item
  {motivation - currently there is a lot of work repeated every year,
  and with very little knowledge preserved (institutional memory), which
  takes up CS dept resources. Lots of tasks could be automated. Personal
  motivation: enjoyed the course, especially these assignments}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Problem Background / related work}{~- past years, harvard, 4.5}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Related work: this course has had programming assignments for years}
\item
  {Related work: 126/226 have automated all of this for years}
\item
  {Related work: Harvard also has AGT PA games (nobody else does)}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {approach - big picture? 3 \textless{}- {[}1-8{]}}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Design of my solution, how it differs}
\item
  {Introduce present / future split}
\item
  {Design and implementation of assignments / design and implementation
  of frameworks for implementing assignments}
\item
  {product component overview}
\item
  {- iterate, provide resources}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Implementation - details important to achieving goal. Keys to
  success. How+why 10}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {~- language choice}
\item
  {sharing code between tesitng / leaderboard / submit / grader (focus
  on modularity)}
\item
  {Sharing code between programming assignments to make new assignment
  development easier}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Evaluation 5.5}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {results - current use in 445}
\item
  {Use next year in 445}
\item
  {Performance evaluation by user studies}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Student reviews}
\item
  {Grader reviews (myself, Matt)}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Conclusions 1.25}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {What will I have to do next year that I didn't have to do this year?}
\item
  {What will I have to repeat next year?}
\item
  {What would I need to tell someone so they would know how ot do this?}
\item
  {future work - next year}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Bibliography}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Collaboration with Matt to co-write the programming assignment specs
  I would be following during `present' work}
\item
  {Note I was paid for some of my time grading (included copying grades
  around when I hadn't finished some of the formatting in the
  autograder, but not developing the autograder)}
\item
  {acknowledgements - thanks matt, cyril, dave, other students in my
  seminar, students in course, UCAs and grad students}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {}
\end{itemize}

{}

{Introduction~~~~~~~~}

{Professor Weinberg's COS 445 (Economics and
Computing)}\textsuperscript{\protect\hyperlink{ftnt1}{{[}1{]}}}{~taught
Spring 2017 was one of the most popular theory classes this department
has ever
taught.}\textsuperscript{\protect\hyperlink{ftnt2}{{[}2{]}}}{~Despite
its classification as a `theory' distribution, the course contains
several programming challenges. In these assignments, students to apply
theoretical results on iterated games and auctions to design and
implement strategies which play iterated games or participate in
auctions. The submissions are then tested against each other and against
instructor strategies. Student feedback emphasized the role of the
programming exercises in the popularity of the
course.}\textsuperscript{\protect\hyperlink{ftnt3}{{[}3{]}}}{~However,
only two of the eight problem sets contained programming exercises in
Spring 2017, and course instructors expressed interest in having a
similar exercise in each problem set. The goal of my project is to
develop new assignments in the same form which develop theoretical
understanding of other topics covered in algorithmic game theory, to
expand the resources available to students completing these assignments,
and to improve the tooling used by instructors for grading student
submissions for these assignments. }

{Problem Background and Related Work}

{This work will be heavily based on the two programming exercises most
recently maintained by Cyril Zhang in Spring 2017, described above,
which I completed while enrolled in this course in that semester. These
assignments, as with those I develop, are written in Java, as dictated
by the prerequisites of the course. Similar assignments have been
developed for Harvard's course by the same
title,}\textsuperscript{\protect\hyperlink{ftnt4}{{[}4{]}}}{~in which
students develop a BitTorrent simulation and auction bidding agents in
Python. However, a brief survey of courses in algorithmic game theory at
other universities, including
Stanford}\textsuperscript{\protect\hyperlink{ftnt5}{{[}5{]}}}{,
Cornell}\textsuperscript{\protect\hyperlink{ftnt6}{{[}6{]}}}{, U.
Washington}\textsuperscript{\protect\hyperlink{ftnt7}{{[}7{]}}}{,
Yale}\textsuperscript{\protect\hyperlink{ftnt8}{{[}8{]}}}{,
Penn}\textsuperscript{\protect\hyperlink{ftnt9}{{[}9{]}}}{, Georgia
Tech}\textsuperscript{\protect\hyperlink{ftnt10}{{[}10{]}}}{, Carnegie
Mellon}\textsuperscript{\protect\hyperlink{ftnt11}{{[}11{]}}}{,
Duke}\textsuperscript{\protect\hyperlink{ftnt12}{{[}12{]}}}{, found no
other results.}

{~~~~~~~~Because of the urgent need for an assistant who can program and
maintain the existing programming challenges for the current semester,
Professor Weinberg and I decided to use the developed assignments
directly as a component of the Spring 2018 instance of COS 445. Thus, I
have a unique opportunity to organize my independent work around live
student feedback, which will be incorporated into the development of
later assignments.}

{~~~~~~~~Potential assignment topics include college admissions (using
stable matchings), elections, and blockchain incentives. The design of
the assignments and instructor solutions will be done under supervision
and lead of Professor Weinberg: we will both brainstorm potential
assignments, and then select for implementation the one we think best
engages students. I will be primarily responsible for developing the
software interfaces for students to design against, the instructor
tooling for quantitative and qualitative evaluation of student
submissions, and the student tooling for simulating and testing their
assignments. The student tooling will allow students to test their
programs in assignments which simulate the real evaluation environment.
I will also be providing support to students who are completing the
assignments and organizing the usage of the instructor evaluation tools.
If time permits, I would like to develop an online leaderboard connected
to the CS Dropbox to allow students to compare their submissions against
each other in real time before the submission deadline.}

{Evaluation}

{I will request feedback from current students about their overall
satisfaction with the programming assignments as compared to additional
theoretical problems (which are still the assignment backbone), their
usage of my tools, and their general suggestions, to improve subsequent
assignments. I will also request feedback from Professor Weinberg and
the undergraduate graders of the course regarding how to provide better
instructor-side tooling for the assignments. My success will be valuable
through students' self-perceived ability to focus on the core assignment
content without experiencing undue difficulties with the assignment
structure and through instructors' present and future usage of the
developed ~assignments. Qualitative measures of success include elements
of survey results described above, decrease in illegal (i.e. errors
unrelated to course content) programs submitted as measured by
anonymized metrics such as lower-outlier rates in quantitative
simulation performance of student submissions, and decrease in
instructor resources (e.g. time) required to maintain and grade the
assignments. These data can be compared to similar data from the two
similar exercises assigned in previous years.}

{Big mistake in `present' - bad at communicating how students would be
graded}

{In the first three weeks of the semester, I have already developed,
implemented, and deployed two assignments, and have developed all of the
tools necessary for grading submissions. I am currently collecting the
completed tools into one automated script which will be able to produce
collated student results and to aggregate results into graphics for
presentation. Preliminary data suggests that rate of illegal submissions
has dropped dramatically with the availability to students of improved
testing software.}

{}

{}

{Framing:}

{-design assignments vs building assignment infrastructure}

{- present vs future}

{-'do it, do it right, do it again' (modularity, extensibility,
reusability)}

{-Components: student testing script, dropbox testing script,
leaderboard script, grader script, sample strategies, instructor
strategies. 4/6 reuasable}

{How are the programming assignments graded? Why were we not informed of
how they would be graded for the first two problem sets?}

{Here is a link to the grading policies sheet for programming
assignments: GradesForProgramming.pdf. This document was in the General
Resources section of the Piazza resources page, referred to from the
programming assignment description for both problem sets (although the
reference was confusing). Survey results indicate that we didn't
properly advertise it and most students were not aware of its existence.
Thus, a lot of students were surprised that the objective questions and
the strength of the writeup were the dominant factors in their grades
-\/-\/- not the performance of their software. Given that we did a poor
job making this clear, we'll be altering how these two assignments are
included in your final grade. See @394 for details.}

{What is the role of programming in a theory course?}

{Survey results indicate at least a few students are confused why they
need to program in a theory course. One key difference between COS 445
(being a theoretical computer science course on game theory) and ECO
418, MAT 378, or POL 347 (other game theory courses offered at
Princeton) is that we place some emphasis on the connections between
game-theoretic results and algorithms, software, and other aspects of
computer science. One way in which we do this is by asking students to
connect their learning in this course to their learning in prerequisite
courses, in this case COS 226. Past course feedback was overwhelmingly
positive for programming challenges (so the hope is that the initial
negative feedback this cycle is due more to poor administration)}

{Here's what we didn't make clear: the "programming assignments" aren't
really about your ability to code. They are about placing the
theoretical results from the course in context. They create a scenario
in which mastery of theoretical results from the course content is
demonstrated by making and justifying real-world decisions. However (and
we didn't communicate this well), we are still grading your response to
the programming exercises as a theory problem. That is why 2/3 of the
credit on the "programming exercises" goes to the theoretical questions,
and why poor performance of your software strategy (so long as it does
not crash) can be entirely offset by a well-written writeup. So, in
actuality, 0\% of your grade is solely dependent on your programming
ability -\/-\/- as is appropriate in a theory course! We include the
empirical performance of your strategy in a way that can only benefit
your grade in the course, to reward students who demonstrated mastery of
the course content by designing a great strategy even if they did not
describe it perfectly}

{Why do we have to use Java (not Python)?}

{We would love to do these assignments in Python, as many students
requested, but unfortunately we do not have Python experience as a
course prerequisite and are firmly of the conviction that it is
inappropriate for a course to expect students to learn a programming
language they have never seen before with no formal instruction (no
matter how many other courses do that).}

{Additionally, empirical data from other course surveys suggests that
90\% of students report themselves fluent in Java after the Princeton
introductory sequence, compared to 30\% for python.}

{Why are my strategies graded against instructor strategies instead of
against the strategies of my peers?}

{We do not believe it is right to grade students against their peers'
submissions because academic performance should not be a zero-sum game.
This was overwhelmingly requested by last year's class.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\protect\hyperlink{ftnt_ref1}{{[}1{]}}{~}{\href{https://www.google.com/url?q=https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm\&sa=D\&ust=1522867200381000}{https://www.cs.princeton.edu/\textasciitilde{}smattw/Teaching/cos445sp17.htm}}

\protect\hyperlink{ftnt_ref2}{{[}2{]}}{~}{\href{https://www.google.com/url?q=https://www.princetoncourses.com/course/1174012095\&sa=D\&ust=1522867200381000}{https://www.princetoncourses.com/course/1174012095}}

\protect\hyperlink{ftnt_ref3}{{[}3{]}}{~Ibid.}

\protect\hyperlink{ftnt_ref4}{{[}4{]}}{~}{\href{https://www.google.com/url?q=https://beta.blogs.harvard.edu/k108875/assignments/\&sa=D\&ust=1522867200386000}{https://beta.blogs.harvard.edu/k108875/assignments/}}

\protect\hyperlink{ftnt_ref5}{{[}5{]}}{~}{\href{https://www.google.com/url?q=https://theory.stanford.edu/~tim/364a.html\&sa=D\&ust=1522867200382000}{https://theory.stanford.edu/\textasciitilde{}tim/364a.html}}

{\href{https://www.google.com/url?q=https://theory.stanford.edu/~tim/f16/f16.html\&sa=D\&ust=1522867200382000}{https://theory.stanford.edu/\textasciitilde{}tim/f16/f16.html}}

\protect\hyperlink{ftnt_ref6}{{[}6{]}}{~}{\href{https://www.google.com/url?q=https://www.cs.cornell.edu/courses/cs6840/2014sp/\&sa=D\&ust=1522867200383000}{https://www.cs.cornell.edu/courses/cs6840/2014sp/}}

\protect\hyperlink{ftnt_ref7}{{[}7{]}}{~}{\href{https://www.google.com/url?q=https://courses.cs.washington.edu/courses/cse522/05sp/\&sa=D\&ust=1522867200383000}{https://courses.cs.washington.edu/courses/cse522/05sp/}}

\protect\hyperlink{ftnt_ref8}{{[}8{]}}{~}{\href{https://www.google.com/url?q=https://zoo.cs.yale.edu/classes/cs455/fall11/\&sa=D\&ust=1522867200384000}{https://zoo.cs.yale.edu/classes/cs455/fall11/}}

\protect\hyperlink{ftnt_ref9}{{[}9{]}}{~}{\href{https://www.google.com/url?q=https://www.cis.upenn.edu/~aaroth/courses/agtS15.html\&sa=D\&ust=1522867200384000}{https://www.cis.upenn.edu/\textasciitilde{}aaroth/courses/agtS15.html}}

\protect\hyperlink{ftnt_ref10}{{[}10{]}}{~}{\href{https://www.google.com/url?q=https://web.archive.org/web/20131002121909/http://www.cc.gatech.edu/\%257Eninamf/LGO10/index.html\&sa=D\&ust=1522867200384000}{https://web.archive.org/web/20131002121909/http://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}}

\protect\hyperlink{ftnt_ref11}{{[}11{]}}{~}{\href{https://www.google.com/url?q=http://www.cs.cmu.edu/~arielpro/15896s16/index.html\&sa=D\&ust=1522867200385000}{http://www.cs.cmu.edu/\textasciitilde{}arielpro/15896s16/index.html}}

\protect\hyperlink{ftnt_ref12}{{[}12{]}}{~}{\href{https://www.google.com/url?q=https://www2.cs.duke.edu/courses/spring16/compsci590.4/\&sa=D\&ust=1522867200385000}{https://www2.cs.duke.edu/courses/spring16/compsci590.4/}}

\end{document}

### 2018-05-02 paper.tex
bunch o files

\documentclass[pageno]{jpaper}

\newcommand{\IWreport}{2016}
\newcommand{\quotes}[1]{``#1''}

\widowpenalty=9999

\usepackage[normalem]{ulem}

\begin{document}

\title{
A Latex Template for Independent Work Reports\\
Version 2016v3}

\author{Firstname Lastname\\Adviser: Firstname Lastname}

\date{}
\maketitle

\thispagestyle{empty}
\doublespacing
\begin{abstract}
This document is intended to serve as a sample you can use for independent work reports.  We provide some guidelines on content and formatting.  They are not required, but they might be helpful.
\end{abstract}

Teaching Algorithmic Game Theory with Programming Competitions
Andrew Wonnacott
COS 398 IW 09 (Professor Walker)
Abstract
Framing: Developing A Modular Framework for Developing, Deploying, and Evaluating programming Assignments in a theory course
Introduction 1.5
goal (1st par) - helping improve the quality of theory eduction for broader cs majors - what will I contribute?
motivation - currently there is a lot of work repeated every year, and with very little knowledge preserved (institutional memory), which takes up CS dept resources. Lots of tasks could be automated. Personal motivation: enjoyed the course, especially these assignments
Problem Background / related work - past years, harvard, 4.5
Related work: this course has had programming assignments for years
Related work: 126/226 have automated all of this for years
Related work: Harvard also has AGT PA games (nobody else does)
approach - big picture? 3 <- [1-8]
Design of my solution, how it differs
Introduce present / future split
Design and implementation of assignments / design and implementation of frameworks for implementing assignments
product component overview
- iterate, provide resources
Implementation - details important to achieving goal. Keys to success. How+why 10
 - language choice
sharing code between tesitng / leaderboard / submit / grader (focus on modularity)
Sharing code between programming assignments to make new assignment development easier
Evaluation 5.5
results - current use in 445
Use next year in 445
Performance evaluation by user studies
Student reviews
Grader reviews (myself, Matt)
Conclusions 1.25
What will I have to do next year that I didn’t have to do this year?
What will I have to repeat next year?
What would I need to tell someone so they would know how ot do this?
future work - next year
Bibliography
Collaboration with Matt to co-write the programming assignment specs I would be following during ‘present’ work
Note I was paid for some of my time grading (included copying grades around when I hadn’t finished some of the formatting in the autograder, but not developing the autograder)
acknowledgements - thanks matt, cyril, dave, other students in my seminar, students in course, UCAs and grad students

Introduction    
Professor Weinberg’s COS 445 (Economics and Computing) taught Spring 2017 was one of the most popular theory classes this department has ever taught. Despite its classification as a ‘theory’ distribution, the course contains several programming challenges. In these assignments, students to apply theoretical results on iterated games and auctions to design and implement strategies which play iterated games or participate in auctions. The submissions are then tested against each other and against instructor strategies. Student feedback emphasized the role of the programming exercises in the popularity of the course. However, only two of the eight problem sets contained programming exercises in Spring 2017, and course instructors expressed interest in having a similar exercise in each problem set. The goal of my project is to develop new assignments in the same form which develop theoretical understanding of other topics covered in algorithmic game theory, to expand the resources available to students completing these assignments, and to improve the tooling used by instructors for grading student submissions for these assignments. 
Problem Background and Related Work
This work will be heavily based on the two programming exercises most recently maintained by Cyril Zhang in Spring 2017, described above, which I completed while enrolled in this course in that semester. These assignments, as with those I develop, are written in Java, as dictated by the prerequisites of the course. Similar assignments have been developed for Harvard’s course by the same title, in which students develop a BitTorrent simulation and auction bidding agents in Python. However, a brief survey of courses in algorithmic game theory at other universities, including Stanford, Cornell, U. Washington, Yale, Penn, Georgia Tech, Carnegie Mellon, Duke, found no other results.
    Because of the urgent need for an assistant who can program and maintain the existing programming challenges for the current semester, Professor Weinberg and I decided to use the developed assignments directly as a component of the Spring 2018 instance of COS 445. Thus, I have a unique opportunity to organize my independent work around live student feedback, which will be incorporated into the development of later assignments.
    Potential assignment topics include college admissions (using stable matchings), elections, and blockchain incentives. The design of the assignments and instructor solutions will be done under supervision and lead of Professor Weinberg: we will both brainstorm potential assignments, and then select for implementation the one we think best engages students. I will be primarily responsible for developing the software interfaces for students to design against, the instructor tooling for quantitative and qualitative evaluation of student submissions, and the student tooling for simulating and testing their assignments. The student tooling will allow students to test their programs in assignments which simulate the real evaluation environment. I will also be providing support to students who are completing the assignments and organizing the usage of the instructor evaluation tools. If time permits, I would like to develop an online leaderboard connected to the CS Dropbox to allow students to compare their submissions against each other in real time before the submission deadline.
Evaluation
I will request feedback from current students about their overall satisfaction with the programming assignments as compared to additional theoretical problems (which are still the assignment backbone), their usage of my tools, and their general suggestions, to improve subsequent assignments. I will also request feedback from Professor Weinberg and the undergraduate graders of the course regarding how to provide better instructor-side tooling for the assignments. My success will be valuable through students’ self-perceived ability to focus on the core assignment content without experiencing undue difficulties with the assignment structure and through instructors’ present and future usage of the developed  assignments. Qualitative measures of success include elements of survey results described above, decrease in illegal (i.e. errors unrelated to course content) programs submitted as measured by anonymized metrics such as lower-outlier rates in quantitative simulation performance of student submissions, and decrease in instructor resources (e.g. time) required to maintain and grade the assignments. These data can be compared to similar data from the two similar exercises assigned in previous years.
Big mistake in ‘present’ - bad at communicating how students would be graded
In the first three weeks of the semester, I have already developed, implemented, and deployed two assignments, and have developed all of the tools necessary for grading submissions. I am currently collecting the completed tools into one automated script which will be able to produce collated student results and to aggregate results into graphics for presentation. Preliminary data suggests that rate of illegal submissions has dropped dramatically with the availability to students of improved testing software.

Framing:
-design assignments vs building assignment infrastructure
- present vs future
-’do it, do it right, do it again’ (modularity, extensibility, reusability)
-Components: student testing script, dropbox testing script, leaderboard script, grader script, sample strategies, instructor strategies. 4/6 reuasable
How are the programming assignments graded? Why were we not informed of how they would be graded for the first two problem sets?
Here is a link to the grading policies sheet for programming assignments: GradesForProgramming.pdf. This document was in the General Resources section of the Piazza resources page, referred to from the programming assignment description for both problem sets (although the reference was confusing). Survey results indicate that we didn't properly advertise it and most students were not aware of its existence. Thus, a lot of students were surprised that the objective questions and the strength of the writeup were the dominant factors in their grades --- not the performance of their software. Given that we did a poor job making this clear, we'll be altering how these two assignments are included in your final grade. See @394 for details.
What is the role of programming in a theory course?
Survey results indicate at least a few students are confused why they need to program in a theory course. One key difference between COS 445 (being a theoretical computer science course on game theory) and ECO 418, MAT 378, or POL 347 (other game theory courses offered at Princeton) is that we place some emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science. One way in which we do this is by asking students to connect their learning in this course to their learning in prerequisite courses, in this case COS 226. Past course feedback was overwhelmingly positive for programming challenges (so the hope is that the initial negative feedback this cycle is due more to poor administration)
Here's what we didn't make clear: the "programming assignments" aren't really about your ability to code. They are about placing the theoretical results from the course in context. They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions. However (and we didn't communicate this well), we are still grading your response to the programming exercises as a theory problem. That is why 2/3 of the credit on the "programming exercises" goes to the theoretical questions, and why poor performance of your software strategy (so long as it does not crash) can be entirely offset by a well-written writeup. So, in actuality, 0% of your grade is solely dependent on your programming ability --- as is appropriate in a theory course! We include the empirical performance of your strategy in a way that can only benefit your grade in the course, to reward students who demonstrated mastery of the course content by designing a great strategy even if they did not describe it perfectly
Why do we have to use Java (not Python)?
We would love to do these assignments in Python, as many students requested, but unfortunately we do not have Python experience as a course prerequisite and are firmly of the conviction that it is inappropriate for a course to expect students to learn a programming language they have never seen before with no formal instruction (no matter how many other courses do that).
Additionally, empirical data from other course surveys suggests that 90% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30% for python.
Why are my strategies graded against instructor strategies instead of against the strategies of my peers?
We do not believe it is right to grade students against their peers' submissions because academic performance should not be a zero-sum game. This was overwhelmingly requested by last year's class.

\section{Ethics}

Your independent work report should abide by the basic standards of scholarly ethics and by the Princeton Honor Code. If you have any doubts about how to cite
other work, how to quote or include text or images from other works, or other issues, please discuss them with your project adviser or with the IW coordinators.

\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
\bibliographystyle{IEEEtranS}
\bibliography{references}

\end{document}

### 2018-05-03 paper.tex
Related Work

@@
 
-\newcommand{\IWreport}{2016}
+\newcommand{\Semester}{Spring}
+\newcommand{\IWreport}{2018}
 \newcommand{\quotes}[1]{``#1''}
@@
 \title{
-A Latex Template for Independent Work Reports\\
-Version 2016v3}
+A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises}
 
-\author{Firstname Lastname\\Adviser: Firstname Lastname}
+\author{Andrew Wonnacott\\
+  Advisers: Professor Dave Walker, Professor Matt Weinberg}
 
@@
 \thispagestyle{empty}
-\doublespacing
+\doublespacing{}
 \begin{abstract}
-This document is intended to serve as a sample you can use for independent work reports.  We provide some guidelines on content and formatting.  They are not required, but they might be helpful.
+  Student interest in Princeton's undergraduate course in algorithmic game theory, ``Economics and Computing'' (COS 445), has grown rapidly in recent years.
+  This course employs small simulations to develop students' ability to use theoretical tools to analyze more real-world situations.
+  These strategy design exercises require considerably more software infrastructure than would a usual theoretical problem set, including handout code for student self-evaluation and software autograders.
+  While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly structured assignments and evaluating student submissions in the context of each other.
+  In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary compoenents oif these strategy design assignments.
+  Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
+  This provides feedback from real student and instructor users which was used to improve the design.
+  Empirical results demonstrate the importance of quality tooling to effective use of instructor time, low broken submission rates, and high student satisfaction.
 \end{abstract}
 
-Teaching Algorithmic Game Theory with Programming Competitions
-Andrew Wonnacott
-COS 398 IW 09 (Professor Walker)
-Abstract
-Framing: Developing A Modular Framework for Developing, Deploying, and Evaluating programming Assignments in a theory course
-Introduction 1.5
-goal (1st par) - helping improve the quality of theory eduction for broader cs majors - what will I contribute?
-motivation - currently there is a lot of work repeated every year, and with very little knowledge preserved (institutional memory), which takes up CS dept resources.
-Lots of tasks could be automated.
-Personal motivation: enjoyed the course, especially these assignments
-Problem Background / related work - past years, harvard, 4.5
-Related work: this course has had programming assignments for years
-Related work: 126/226 have automated all of this for years
-Related work: Harvard also has AGT PA games (nobody else does)
-approach - big picture? 3 <- [1-8]
-Design of my solution, how it differs
-Introduce present / future split
-Design and implementation of assignments / design and implementation of frameworks for implementing assignments
-product component overview
-- iterate, provide resources
-Implementation - details important to achieving goal. Keys to success. How+why 10
- - language choice
-sharing code between tesitng / leaderboard / submit / grader (focus on modularity)
-Sharing code between programming assignments to make new assignment development easier
-Evaluation 5.5
-results - current use in 445
-Use next year in 445
-Performance evaluation by user studies
-Student reviews
-Grader reviews (myself, Matt)
-Conclusions 1.25
-What will I have to do next year that I didn’t have to do this year?
-What will I have to repeat next year?
-What would I need to tell someone so they would know how ot do this?
-future work - next year
-Bibliography
-Collaboration with Matt to co-write the programming assignment specs I would be following during ‘present’ work
-Note I was paid for some of my time grading (included copying grades around when I hadn’t finished some of the formatting in the autograder, but not developing the autograder)
-acknowledgements - thanks matt, cyril, dave, other students in my seminar, students in course, UCAs and grad students
+\newpage
+\section*{Introduction}
+\begin{itemize}
+\item Discussion of strategy design assignments on cos445sp1[78] with specific examples (from this year + PD)
+\item Mention how they are graded (not zero-sum)
+\item While these assignments were popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demanded considerable instructor resources be dedicated to building and grading software resoruces.
+Additionally, due to the limited tooling provided for students to evaluate their submissions, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
+\end{itemize}
 
-Introduction    
-Professor Weinberg’s COS 445 (Economics and Computing) taught Spring 2017 was one of the most popular theory classes this department has ever taught.
-Despite its classification as a ‘theory’ distribution, the course contains several programming challenges.
-In these assignments, students to apply theoretical results on iterated games and auctions to design and implement strategies which play iterated games or participate in auctions.
-The submissions are then tested against each other and against instructor strategies.
-Student feedback emphasized the role of the programming exercises in the popularity of the course.
-However, only two of the eight problem sets contained programming exercises in Spring 2017, and course instructors expressed interest in having a similar exercise in each problem set.
-The goal of my project is to develop new assignments in the same form which develop theoretical understanding of other topics covered in algorithmic game theory, to expand the resources available to students completing these assignments, and to improve the tooling used by instructors for grading student submissions for these assignments.
-Problem Background and Related Work
-This work will be heavily based on the two programming exercises most recently maintained by Cyril Zhang in Spring 2017, described above, which I completed while enrolled in this course in that semester.
-These assignments, as with those I develop, are written in Java, as dictated by the prerequisites of the course.
-Similar assignments have been developed for Harvard’s course by the same title, in which students develop a BitTorrent simulation and auction bidding agents in Python.
-However, a brief survey of courses in algorithmic game theory at other universities, including Stanford, Cornell, U.
-Washington, Yale, Penn, Georgia Tech, Carnegie Mellon, Duke, found no other results.
-    Because of the urgent need for an assistant who can program and maintain the existing programming challenges for the current semester, Professor Weinberg and I decided to use the developed assignments directly as a component of the Spring 2018 instance of COS 445.
-Thus, I have a unique opportunity to organize my independent work around live student feedback, which will be incorporated into the development of later assignments.
-    Potential assignment topics include college admissions (using stable matchings), elections, and blockchain incentives.
-The design of the assignments and instructor solutions will be done under supervision and lead of Professor Weinberg: we will both brainstorm potential assignments, and then select for implementation the one we think best engages students.
-I will be primarily responsible for developing the software interfaces for students to design against, the instructor tooling for quantitative and qualitative evaluation of student submissions, and the student tooling for simulating and testing their assignments.
-The student tooling will allow students to test their programs in assignments which simulate the real evaluation environment.
-I will also be providing support to students who are completing the assignments and organizing the usage of the instructor evaluation tools.
-If time permits, I would like to develop an online leaderboard connected to the CS Dropbox to allow students to compare their submissions against each other in real time before the submission deadline.
-Evaluation
-I will request feedback from current students about their overall satisfaction with the programming assignments as compared to additional theoretical problems (which are still the assignment backbone), their usage of my tools, and their general suggestions, to improve subsequent assignments.
-I will also request feedback from Professor Weinberg and the undergraduate graders of the course regarding how to provide better instructor-side tooling for the assignments.
-My success will be valuable through students’ self-perceived ability to focus on the core assignment content without experiencing undue difficulties with the assignment structure and through instructors’ present and future usage of the developed  assignments.
-Qualitative measures of success include elements of survey results described above, decrease in illegal (i.e.
-errors unrelated to course content) programs submitted as measured by anonymized metrics such as lower-outlier rates in quantitative simulation performance of student submissions, and decrease in instructor resources (e.g.
-time) required to maintain and grade the assignments.
-These data can be compared to similar data from the two similar exercises assigned in previous years.
-Big mistake in ‘present’ - bad at communicating how students would be graded
-In the first three weeks of the semester, I have already developed, implemented, and deployed two assignments, and have developed all of the tools necessary for grading submissions.
-I am currently collecting the completed tools into one automated script which will be able to produce collated student results and to aggregate results into graphics for presentation.
-Preliminary data suggests that rate of illegal submissions has dropped dramatically with the availability to students of improved testing software.
+\section*{Related Work}
+This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
+In one problem set, students developed and implemented strategies for three different strategy design exercises, related to three different classical games: Prisoner's Dilemma, Centipede, and Ultimatum.
+In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid.
+This is the auction format used by Google to sell sponsored search auctions.}
 
-Framing:
--design assignments vs building assignment infrastructure
-- present vs future
--’do it, do it right, do it again’ (modularity, extensibility, reusability)
--Components: student testing script, dropbox testing script, leaderboard script, grader script, sample strategies, instructor strategies. 4/6 reuasable
-How are the programming assignments graded? Why were we not informed of how they would be graded for the first two problem sets?
-Here is a link to the grading policies sheet for programming assignments: GradesForProgramming.pdf.
-This document was in the General Resources section of the Piazza resources page, referred to from the programming assignment description for both problem sets (although the reference was confusing).
-Survey results indicate that we didn't properly advertise it and most students were not aware of its existence.
-Thus, a lot of students were surprised that the objective questions and the strength of the writeup were the dominant factors in their grades --- not the performance of their software.
-Given that we did a poor job making this clear, we'll be altering how these two assignments are included in your final grade.
-See @394 for details.
-What is the role of programming in a theory course?
-Survey results indicate at least a few students are confused why they need to program in a theory course.
-One key difference between COS 445 (being a theoretical computer science course on game theory) and ECO 418, MAT 378, or POL 347 (other game theory courses offered at Princeton) is that we place some emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
-One way in which we do this is by asking students to connect their learning in this course to their learning in prerequisite courses, in this case COS 226.
-Past course feedback was overwhelmingly positive for programming challenges (so the hope is that the initial negative feedback this cycle is due more to poor administration)
-Here's what we didn't make clear: the "programming assignments" aren't really about your ability to code.
-They are about placing the theoretical results from the course in context.
-They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.
-However (and we didn't communicate this well), we are still grading your response to the programming exercises as a theory problem.
-That is why 2/3 of the credit on the "programming exercises" goes to the theoretical questions, and why poor performance of your software strategy (so long as it does not crash) can be entirely offset by a well-written writeup.
-So, in actuality, 0% of your grade is solely dependent on your programming ability --- as is appropriate in a theory course!
-We include the empirical performance of your strategy in a way that can only benefit your grade in the course, to reward students who demonstrated mastery of the course content by designing a great strategy even if they did not describe it perfectly
-Why do we have to use Java (not Python)?
-We would love to do these assignments in Python, as many students requested, but unfortunately we do not have Python experience as a course prerequisite and are firmly of the conviction that it is inappropriate for a course to expect students to learn a programming language they have never seen before with no formal instruction (no matter how many other courses do that).
-Additionally, empirical data from other course surveys suggests that 90% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30% for python.
-Why are my strategies graded against instructor strategies instead of against the strategies of my peers?
-We do not believe it is right to grade students against their peers' submissions because academic performance should not be a zero-sum game. This was overwhelmingly requested by last year's class.
+Both problem sets were implemented and graded by Cyril Zhang\footnote{https://github.com/cyrilzhang}, a graduate student TA for the course.
+Cyril developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
+However, this existing implementation of grader software for strategy design assignments is not modular and has to be completely rewritten for each assignment, and was designed for grader use only.
+The student interfaces were documented, but the grader software was not documented for future re-use.
+Additionally, some of the scripts and notebooks used by Cyril were not preserved and were not accessible as resources.
+Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Cyril's code.
 
-\section{Ethics}
+Previous to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
+Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code respositories used by the course staff.
+In both semesters, Yonatan Naamad\footnote{https://github.com/ynaamad/} was responsible for software development.
 
-Your independent work report should abide by the basic standards of scholarly ethics and by the Princeton Honor Code. If you have any doubts about how to cite
-other work, how to quote or include text or images from other works, or other issues, please discuss them with your project adviser or with the IW coordinators.
+The only resources available from Fall 2012 were collected from the course Google Code repository.\footnote{https://code.google.com/archive/p/cos445-scripts/}
+This repository contains incomplete Python skeleton code for a basic tournament.
+This was uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but was not reused.
 
-\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
-\bibliographystyle{IEEEtranS}
-\bibliography{references}
+The Spring 2014 iteration of the course was developed on a private GitHub repository.\footnote{https://github.com/ynaamad/cos445}
+Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
+The Java code consisted of student handouts of interfaces and some testing code, but the testing code was not designed to be automated for grading and was not modular: it tested manually-enterred strategies against each other and assignment-specific details (e.g.\ game structure and payoffs) were integrated within the simulation code.
+As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
+These resources were uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.
+
+Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
+However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.
+Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.
+Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.
+
+Harvard's Computer Science 136, ``Economics and Computation'',\footnote{https://beta.blogs.harvard.edu/k108875/assignments/} assigns two programming problem sets.
+The first requires implementation of a peer-to-peer filesharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
+However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
+The second assignment is a strategy design exercise built on the generalized second-price auction, in which student strategies vary and are graded based on their performance in a competitive environment.
+This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
+However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and the implementation is in Python.
+While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
+Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445 at Princeton.
+
+Many universities, including Princeton, maintain extensive systems for the automatic submission and processing of student assignments.
+Such resources are useful in the general case of developing new programming-based assignments, but no such resources replicate the behavior implemented in this project.
+Most autograding systems are designed with an assumption that student submission are graded in a sandbox, isolated from other student submissions.
+Such systems are not applicable to this project, since the strategy design exercises involve evaluation of student strategy performance in a common environment.
+However, existing resources for assignment submission and student feedback in use by Princeton are used in this assignment.
+I integrated some CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and modelled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
+Generally, however, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.
+
+\section*{Conclusions}
+prisoner's dilemma + search auctions
+
+\section*{Future Work}
+
+Some of the implementations of my infrastructure could be simplified using ClassLoaders, which would replace some of the Python code.
+This improvement was inspired by the implementation of ClassLoaders in the Spring 2014 student handout code.
+
+Earlier assignments were built off of earlier versions of the infrastructure and will need to be ported to newer versions when they are reused
 

### 2018-05-03 template.tex
Related Work

\documentclass[pageno]{jpaper}

\newcommand{\Semester}{Fall}
\newcommand{\IWreport}{2016}
\newcommand{\quotes}[1]{``#1''}

\widowpenalty=9999

\usepackage[normalem]{ulem}

\begin{document}

\title{
A Latex Template for Independent Work Reports\\
Version 2016v3}

\author{Firstname Lastname\\Adviser: Firstname Lastname}

\date{}
\maketitle

\thispagestyle{empty}
\doublespacing
\begin{abstract}
This document is intended to serve as a sample you can use for independent work reports.  We provide some guidelines on content and formatting.  They are not required, but they might be helpful.
\end{abstract}

\section{Introduction}

This document is a sample you can use for formatting your independent work
report.  An example template with all bib and supporting files can be downloaded
from the IW website at {\em http://iw.cs.princeton.edu}.

\section{Preparation Instructions}

\subsection{Paper Formatting}
\label{section:formatting}

There are no minimum or maximum length limits on IW reports.  
We are including this template because we think it will be helpful
for citing things properly and for including figures into formatted
text.  If you are using \LaTeX~\cite{lamport94} 
to typeset your paper, then we strongly suggest
that you start from the template available at
http://iw.cs.princeton.edu -- this
document was prepared with that template.  
If you are using a different software package to typeset your paper, 
then you can still use this document as a reasonable sample of 
how your report might look.  Table~\ref{table:formatting} is a suggestion
of some formatting guidelines, as well as being an example of how to
include a table in a Latex document.

\begin{table}[hbt]
  \centering
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Field} & \textbf{Value}\\
    \hline
    \hline
    Paper size & US Letter 8.5in $\times$ 11in\\
    \hline
    Top margin & 1in\\
    \hline
    Bottom margin & 1in\\
    \hline
    Left margin & 1in\\
    \hline
    Right margin & 1in\\
    \hline
    Body font & 12pt\\
    \hline
    Abstract font & 12pt, italicized\\
    \hline
    Section heading font & 14pt, bold\\
    \hline
    Subsection heading font & 12pt, bold\\
    \hline
  \end{tabular}
  \caption{Formatting guidelines. }
  \label{table:formatting}
\end{table}

\textbf{Please ensure that you include page numbers with your
submission}. This makes it easier for readers to refer to
different parts of your paper when they provide comments.

We highly recommend you use bibtex for managing your references and citations.  You can add bib entries to a references.bib file throughout the semester (e.g., as you read papers) and then they will be ready for you to cite when you start writing the report.  If you use bibtex, please note that the references.bib file provided in the template example includes some format-specific incantations at the top of the file.  If you substitute your own bib file, you will probably want to include these 
incantations at the top of it.

\subsection{Citations and Footnotes}

There are various reasons to cite prior work and include it as references in your bibliography.  For example, If you are improving upon 
prior work, you should include
a full citation for the work in the bibliography \cite{nicepaper,nicepaper2}. 
You can also cite information that is used as background or
explanation\cite{Salzberg:2005}.  In addition to citing scholarly papers or books, you can
also create bibtex entries for webpages or other sources.  Many online
databases allow you to download a premade bibtex entry for each paper
you access.  You can simply copy-paste these into your references.bib
file.

Sometimes you want to footnote something, such as a web
site.\footnote{http://www.cs.princeton.edu}  Note that the footnote
number comes after the punctuation.

\subsection{Figures and Tables.}

Figure \ref{fig:gray} shows an example of how to include a figure in
your report.  
Ensure that the figures and
tables are legible.  Please also ensure that you refer to your
figures in the main text. Make sure that your figures will be legible
in the expected forms that the report will be read.  If you expect someone
to print it out in gray-scale, then make sure the figures are legible 
when printed that way.

\begin{figure}[hbt]
\centering
\includegraphics[width=0.75\linewidth]{gray.jpg}
\caption{This is a gray image.}
\label{fig:gray}
\end{figure}

In Section~\ref{section:formatting}, an example of a table was given.
(Note that the ``S'' in Section is capitalized.  Here's one more
example - see Table~\ref{table:data}.

\begin{table}[hbt]
  \centering
  \begin{tabular}{|l|l|} \hline
    \textbf{Some field} & \textbf{Another field}\\\hline
    200          &  10000 \\ \hline 
    400          &  20000 \\ \hline 
    800          &  40000 \\ \hline 
    1600        &  80000 \\ \hline 
    3200        &  160000 \\ \hline 
    6400        &  320000 \\ \hline 
  \end{tabular}
  \caption{Some data in a table. }
  \label{table:data}
\end{table}

Here's an example that shows how you can have side-by-side figures -
see Figure~\ref{fig:side-a} and Figure~\ref{fig:side-b}.  (Note that
the the ``F'' in Figure is capitalized.

\begin{figure}[htbb]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[width=.75\linewidth]{checkerboard-squares-black-white.jpg}
\caption{Plain checkerboard.}
\label{fig:side-a}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[width=.75\linewidth]{swirl-squares-black-white.jpg}
\caption{Cool checkerboard.}
\label{fig:side-b}
\end{minipage}
\end{figure}

\subsection{Double Quotes.}

Latex double quotes are not the same as the double quote key on your
keyboard. The standard way of writing quotes and double quotes in
LaTeX is with `` and '' not with " and ".

Now that may be confusing, so you may want to use the \textbackslash\{quotes\} command.  For
example \quotes{The quick brown fox.}

\subsection{Main Body.}

Avoid bad page or column breaks in
your main text, i.e., last line of a paragraph at the top of a
column or first line of a paragraph at the end of a column. If you
begin a new section or sub-section near the end of a column,
ensure that you have at least two (2)  lines of body text on the same
column.

\section{Outline}  
The following is a possible outline for your paper.
\subsection{Introduction}
\begin{itemize}
\item Motivation and Goal (The goal of this project is...)
\item Overview of challenge and previous work 
\item Approach 
\item Summary of implementation
\item Summary of results
\item (optional) Roadmap: The remainder of this paper is organized as follows....
\end{itemize}

\subsection{Problem Background and Related Work}
\begin{itemize}
\item Survey of prior work with similar goals 
\item For each previous approach, explain what has been done and why it does not meet your goal
\end{itemize}

\subsection{Approach}
\begin{itemize}
\item Key novel idea
\item Why it is a good idea
\end{itemize}

\subsection{Implementation}
\begin{itemize}
\item System overview (flow chart of key steps?)
\item Subsection for each step or issue you addressed
\begin{itemize}
\item Problem statement
\item Possible approaches
\item Chosen approach and why
\item Implementaton details
\end{itemize}
\end{itemize}

\subsection{Evaluation}
\begin{itemize}
\item Experiment design...
\item Data...
\item Metrics...
\item Comparisons...
\item Qualitative results...
\item Quantitative results...
\end{itemize}

\subsection{Summary}
\begin{itemize}
\item Conclusions...
\item Limitations...
\item Future work...
\end{itemize}

\section{Ethics}

Your independent work report should abide by the basic standards of scholarly ethics and by the Princeton Honor Code. If you have any doubts about how to cite
other work, how to quote or include text or images from other works, or other issues, please discuss them with your project adviser or with the IW coordinators.

\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
\bibliographystyle{IEEEtranS}
\bibliography{references}

\end{document}

### 2018-05-04 paper.tex
Start Approach

@@
 
+\section*{Approach}
+Throughout the course of developing this framework, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester.
+That is, in order to develop a reusable toolchain for building strategy design exercises, I have developed strategy design exercises to inform the design and development of a reusable toolchain.
+
 \section*{Conclusions}

### 2018-05-04 paper.tex
Introduction (still a little too background-y)

@@
 \section*{Introduction}
-\begin{itemize}
-\item Discussion of strategy design assignments on cos445sp1[78] with specific examples (from this year + PD)
-\item Mention how they are graded (not zero-sum)
-\item While these assignments were popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demanded considerable instructor resources be dedicated to building and grading software resoruces.
-Additionally, due to the limited tooling provided for students to evaluate their submissions, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
-\end{itemize}
+Four Princeton University departments offer courses in game theory: economics, politics, mathematics, and computer science.
+While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
+For instance, in the computer science department, COS 445, ``Economics and Computing'', places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
+This is represented in the course topics, which focus on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
+It is also represented in the design of the problem sets, which contain, in addition to traditional proof-based exercises, programming-based exercises which connect course topics to prerequesite computer science skills.
+These programming-based exercises take a common form.
+
+Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
+A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java iterface}, in which two players must collaborate to receive the best outcome, but are each incentivized to defect, which results in a less preferred outcome, and have acecss to the other player's play history when making their own decision.
+While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including, from semester to semester, a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
+These examples are not exhaustive, but illustrate the variety of course topics with potential for translation to iterated games.
+
+Students then craft strategies to play the specified game, based on their own analyses of the game's equilbirium, and based on their own priors over the strategies which will be designed by their peers.
+These strategies are evaluated on both on their design quality and on their empirical performance.
+While design quality is evaluated on a purely individual basis, empirical performance is measured by simulating the play of the collection of submitted student strategies.
+For instance, for the iterated prisoner's dilemma, every student strategy plays one full game (consisting of many iterations of the prisoner's dilemma) against each other strategy, and strategies are scored based off the average payoff they achieved.
+For the search advertisement game, all the student strategies are concurrently asked to bid on the same search terms, and are scored based on their revenue from ad clicks (where each bidder knows the click-through rate for a term prior to bidding on that term) less their expenditures on advertising.
+To create a more realistic simulation, students are graded solely the performance of their own strategy, not on a curve of the performance of their peers.
+That is, student grades on these strategy design exercises are not zero-sum.
+
+While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demanded considerable instructor resources be dedicated to building and grading software resoruces, which have historically been significantly rebuilt for each assignment.
+Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
+Due to the limited tooling provided in past semesters for students to evaluate their submissions, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
+
+The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
+This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
+Within this framework, I have built a collection of utilities to facilitate student self-evaluation and decrease strategy iteration overhead.
+
+Through this work, I aim to improve the quality of computer science theory education, from the perspectives of both the students and faculty associated with COS 445.
+Quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
 
@@
 Throughout the course of developing this framework, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester.
+
 That is, in order to develop a reusable toolchain for building strategy design exercises, I have developed strategy design exercises to inform the design and development of a reusable toolchain.
+
+* how to discover what can be modularized
+
+\section*{Implementation}
+* how to modularize that
+
+\section*{Results}
 
@@
 
-Earlier assignments were built off of earlier versions of the infrastructure and will need to be ported to newer versions when they are reused
+Earlier assignments were built off of earlier versions of the infrastructure and will need to be ported to newer versions when they are reused: do next year
+
+will be reused in two years without my oversight
+
+other universities? matt through academic connections
+
+\section*{Acknowledgements}
+
+\section*{Ethics}
+* assignments used in the course were used by the executive decision of Professor Weinberg,
+* potential conflicts of interest
+* honor code
 

### 2018-05-05 paper.tex
Approach

@@
 \section*{Introduction}
+My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course.
+The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally, within healthy incentive structures where students do not try to hurt each others’ performance.
+Each past offering of the course has rebuilt these assignments from scratch, and all associated instructor tooling, resulting in unnecessarily high allocation of instructor time to grading.
+Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
+In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for the students, I develop an extensible framework to improve these strategy design exercises.
+
 Four Princeton University departments offer courses in game theory: economics, politics, mathematics, and computer science.
@@
 The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
-This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
-Within this framework, I have built a collection of utilities to facilitate student self-evaluation and decrease strategy iteration overhead.
+This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
+Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
 
@@
 Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
-However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.
-Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.
-Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.
+However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.
 
@@
 \section*{Approach}
-Throughout the course of developing this framework, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester.
+Cyril Zhang completed the TA requirement for the PhD program last fall, so at the start of this semester it was unclear who among the graduate and undergraduate course staff would be responsible for maintaining these assignments.
+Thus, the course needed not just long-term work to improve student and instructor resources, but also short-term work to maintain and debug the same resources.
+These harmonizing requirement suggest that the product should consist of one extensible implementation of all the reusable components for software design exercises, developed iteratively in conjunction with its usage in the course.
+This software would naturally grow throughout development as demanded by the needs of the course, and the final product will naturally lower-bound the maximum degree of automation and modularity possible.
 
-That is, in order to develop a reusable toolchain for building strategy design exercises, I have developed strategy design exercises to inform the design and development of a reusable toolchain.
+Before the first problem set of the course was assigned in this semester, Matt and I designed and I implemented a handout interface and tools to allow students to test their strategies against each other.
+The game simulates college admissions using stable matchings.
+While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design covered in previous courses.\footnote{Kernighan and Pike chapter 4}
+I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which amortized results from multiple randomized trials, and from agglomerated these results to output performance statistics for students.
+Thus, when it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trails changed from college admissions to elections.
+Additionally, when it came time to grade the problem set, I was able to modify only the post-processing step to compute grades.
+Thus, creating a new assignment requires constant work in the number of framework extensions, and creating a new framework extension requires constant work in the number of assignments.
 
-* how to discover what can be modularized
+The result of this process duplicates significant functionality from last year's assignments.
+However, because of conscious design decisions to factor our repeated code from assignment implementations, it accomplishes what previous implementations had not.
+It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
+Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
+And, it will be reusable, both for the same assignments in future years, and for new strategy design exercises implemented by future course staff with lower overhead.
+
+In order to increase the reusability, I elected to store it in a University-owned private GitHub repository.
+This ensures that, even after I have graduated, future course staff will have access to the project.
+Additionally, I documented the repository structure and each program's role in the repository, as documented later in this document.
 
 \section*{Implementation}
+The first key decision in the implementation of these programming assignments was language selection.
+Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results}, and this would be preferred by the course staff as well.
+Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
+Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parametrized on user-input strategy names.
+Unfortunately, COS 445 does not have Python experience as a course prerequisite, only Java experience.
+Additionally, survey data from other course surveys suggests that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for python.\footnote{COS 333 survey data}
+
+Thus, the whole system under consideration is constrained: it must support student strategy implementations in Java.
+Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignments as possible in Java, with limited usage of scripting languages such as make, Python, and bash.
+These scripting languages were used where Java would not suffice and only for tasks for which implementation details were irrelevant to student assignment comprehension.
+
 * how to modularize that
+* what is reusable
+* what isnt reusable
+This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
+Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
+how to grade people not against peers
+
+* what extensions
 
 \section*{Results}
+As the goals of a project naturally define evaluation criteria, I have evaluated my project on the basis of those goals.
+
+Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
 
 \section*{Conclusions}
+Through this work, I aim to improve the quality of computer science theory education, from the perspectives of both the students and faculty associated with COS 445.
+
 prisoner's dilemma + search auctions
+
+The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
 
@@
 \section*{Acknowledgements}
+* matt for assignment design lead
+* course staff, especially Andreea, Ariel, Evan, Heesu, Leila, Divya, Matheus, Wei, Dylan, for grading student writeups, providing me feedback and passing along student feedback
+* david walker for iw sem (helping me stay organized and on track, helping me identify my topic)
+* iw sem peers Greg, Alex, Mel, Noah for feedback
+* jeremie for creating github repo
+* kate for providing writing help and moral support
 

### 2018-05-05 paper.tex
outline Results

@@
 * what isnt reusable
-This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
-Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
+%This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
+%Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
 how to grade people not against peers
@@
 
-Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
+\begin{itemize}
+\item discover modularity and decrease assignment to assignment rewriting
+  \begin{itemize}
+  \item code rewriting measurements
+  \item instructor time usage
+  \end{itemize}
+\item improve student resources
+  \begin{itemize}
+  \item list resources created
+  \item polling data about student usage
+  \item empirical results about student error rates
+  \end{itemize}
+\item create institutional memory and decrease year-to-year rewriting
+  \begin{itemize}
+  \item cant measure until next year, but set up for it
+  \end{itemize}
+\item increase student and instructor satisfaction
+  \begin{itemize}
+  \item polling data about student usage
+  \end{itemize}
+\end{itemize}
+
+%Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
 
@@
 
-The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
+%The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
+
+%the "programming assignments" aren't really about your ability to code.
+They are about placing the theoretical results from the course in context.
+They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.
 

### 2018-05-05 paper.tex
Write some of implementation, outline rest

@@
 \newcommand{\quotes}[1]{``#1''}
-
-\widowpenalty=9999
+\makeatletter
+\def\verbatim@font{\linespread{1}\normalfont\ttfamily}
+\makeatother
+\clubpenalty9998
+\widowpenalty9999
 
@@
   While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly structured assignments and evaluating student submissions in the context of each other.
-  In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary compoenents oif these strategy design assignments.
+  In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary components of these strategy design assignments.
   Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
@@
 Unfortunately, COS 445 does not have Python experience as a course prerequisite, only Java experience.
-Additionally, survey data from other course surveys suggests that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for python.\footnote{COS 333 survey data}
+Additionally, survey data from other course surveys suggests that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python.\footnote{COS 333 survey data}
 
@@
 
-* how to modularize that
-* what is reusable
-* what isnt reusable
-%This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
-%Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
-how to grade people not against peers
+Java also offers convenience to assignment designers by enforcing an object-oriented design pattern.
+This allows instructors to communicate an assignment specification formally through a well-documented interface.
+Furthermore, by constructing new instances of the student implementations between game rounds, instructors can programatically enforce that students do not employ learning strategies outside the parameters of the assignment.\footnote{This requires that instructors forbid the usage of static variables, but it is trivial to verify compliance with this requirement.}
 
-* what extensions
+However, several default Java behaviors do not map cleanly onto the desired properties of strategy design exercises.
+For instance, Java objects used as function parameters are passed by mutable, nullable reference.
+This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and not null unless otherwise explicitly specified.
+Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html#unmodifiableList(java.util.List)}
+In order to preserve backwards compatibility, these features are not implemented by default.
+Where possible, I have taken advantage of these features.
+Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
+However, I have not included NotNull annotations because they are not taught in the prerequesite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
+In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}
+
+In order to design my framework, I reviewed unmodularized code from a past strategy design exercise, the Spring 2017 auctions exercise.
+This is the only assignment to which I had access to the full implementation of the student handout (having taken the course) and the grader code (preserved by Professor Weinberg).
+The first piece of the assignment to be implemented, after the game design is complete, is the student interface:\footnote{TODO: make this code a figure}
+\begin{verbatim}
+import java.util.List;
+
+public interface Bidder {
+    // Return your bid for the current day
+    // Called once per day before the auction
+    public double getBid(double dailyValue);
+
+    // Let you know if you won, and how much the winners paid
+    // Called once per day after the auction
+    public void addResults(List<Double> bids, int myBid, double myPayment);
+}
+\end{verbatim}
+This interface describes what students' strategies must do: they must, each day, bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results''), and they value the word being auctioned each day at a different value.
+The strategy also has access the winning bids for each of the ten sponsored results from each past day, and knows if it won any auctions itself, and if so how much it paid.
+This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
+These constants are not documented in the interface as designed, only in the assignment specification.
+The instructors distribute a simple sample student implementation, in this case the truthful bidder.
+Cyril also implemented a program used to grade the student-submitted strategies.
+This program had two methods: \texttt{main} and \texttt{trial}.
+The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
+The latter contained an implementation of the generalized second-price auction format described in the assignment specification.
+
+Having reviewed a former assignment, I implemented the first assignment handout for the course this semester: the college admissions simulation described previously.
+In doing so, I made several implementation decisions in order to facilitate future reconfiguration of the game being played and of the postprocessing of the tournament results which are representative of design decisions made throughout the assignment.
+In every assignment, the tournament simulation portion (instructor-written code) is broken up into game rounds, result processing and amortization, and further postprocessing, such as grade assignment and output formatting.
+The divide between game rounds and code which processes game results was present in Cyril's auction code, as the separation between the \texttt{trial} and \texttt{main} methods.
+However, this prior work did minimal amortization and no advanced output formatting, and had no separation between them.
+While the handout code written for the first assignment did minimal postprocessing, this distinction was quite useful when later developing the autograder and additional extensions.
+
+During the development of this handout, however, the statically-typed nature of Java raised some difficulty.
+Cyril's code had student submission names hardcoded into complex expressions, as though they had been copied in from a manually-written list formatted using sed.
+In the context of developing a handout to allow students to test multiple strategies of their own design, I determined requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
+Additionally, graders desire functionality to configure the list of strategies to be evaluated at grading time, without having to manually list out all the student strategy names, and to easily modify this list to identify and diagnose misbehaving student strategies.
+Since Java is not able to type-check user-input strategy names, I determined that the most effective workaround for this issue would be to automatically rewrite the Java code before compile-time.
+
+For this purpose, I developed a simple Python script capable of rewriting arbitrary template plaintext files using a CSV file.
+This script, \texttt{formatBase.py}, builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
+Then, it rewrites its input by finding lines which start with \texttt{//R} and end with \texttt{//}, and replaces each such line with, for each row of the CSV, the line rewritten by replacing each curly-enclosed key with the corresponding value from that row.
+It also rewrites the key \texttt{0} with the row number from the configuration table.
+This script directly injects the contents of the configuration file into the Java code with no escaping, as is necessary in this application.
+However, this practice is extremely dangerous, since using a user-submitted configuration file would allow users to execute arbitrary code on the evaluation machine.
+Fortunately, this is not a security concern, since students already run arbitrary code on the evaluation machine: their submitted strategy.
+
+Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thus rewritten to instantiate one implementation of each Student class listed in the configuration file:
+\footnote{use figure}
+\begin{verbatim}
+    public static int[] oneEachTrial(double S, double T, double W)
+    {
+        // Initialize students
+        Student[] students = new Student[N];
+        //R students[{0}] = new Student_{netID}();//
+        return runTrial(students, S, T, W);
+    }
+\end{verbatim}
+In the above code from the college applications simulator, \texttt{S}, \texttt{T}, and \texttt{W} are configuration parameters for the simulation which were documented in the student interface.
+For contrast, the following method also instantiates an instance of an instructor-provided strategy using reflection.
+This illustrates potential variation in data collection code as enabled by my modular design, and is used in the autograder described below.
+\footnote{todo: figure}
+\begin{verbatim}
+    public static <Student_T extends Student> int[] withExtraTrial(
+            Class<Student_T> clazz, double S, double T, double W)
+    {
+        // Initialize students
+        Student[] students = new Student[N+1];
+        //R students[{0}] = new Student_{netID}();//
+        try {
+            students[N] = clazz.getConstructor().newInstance();
+        } catch (ReflectiveOperationException roe) {
+            roe.printStackTrace();
+            System.exit(1);
+        }
+
+        return runTrial(students, S, T, W);
+    }
+\end{verbatim}
+
+now we can also have a better handout
+outline better handout
+* interface
+* dumb implementation
+* full copy of the above code
+comment on use of formatbase here
+comment on separate files for each assignment - why (simplify handout)
+
+but we wanted a grader. how to build grader from that?
+brief tangent to how to grade, not against peers
+introduce replacement-comparison grading
+* have some instructor strategies designed to perform well
+* substitute, for each student, a copy of each instructor strategy
+* grade based on how many instructor strategies the student's strategy did better than against the same pool
+* comment about incentive structures of this method: correct due to amortization (maximize your expectation to maximize your chance of beating unknown instructor thresholds.
+amortization means your outcome equals your expectation)
+
+issue with this: O(mn) time
+* can cut down to O(m) time by just adding each instructor strategy one by one and seeing how they do against the whole field.
+* assume that each individual student has negligible impact on that instructor's performance.
+* Comment as to whether this is a realistic assumption.
+* comment on incentives of this method - approximately correct as before
+
+back to buidling the grader
+manually write the list of grader strategies
+make a new method very similar to one each trials: with extra trials
+lookup table: how many instructor strategies beat -> score
+didn't need to change the trial at all
+so that doesn't need to be changed when makign a new assignment
+we can now grade every assignment
+
+catch: sometimes we want to simulate multiple parameter settings for student code
+involves changing the main method a bit
+not much change
+
+so now we have a framework which makes it easy to build new assignments
+what really changes?
+build ultimatum
+
+we also have a framework to build new tools
+let's build new tools
+what shoudl we build?
+what problems to address?
+ease of testing
+``Works On My Machine''
+getting a better idea about how a strategy would perform against more realistic collection of peers
+
+dropbox checksubmit
+learned how cs dropbox works
+a little bash + make to copy in the student handout, detect and write a config file to run their code
+show script + makefile
+show an output
+
+leaderboard
+new tools: cycles cron
+simple to copy in all submissions, detect and write config file, run code, post it to website
+discuss issues
+student code breaking it
+harden the tester (try catch around each student with selfless behavior)
+student code causing compile failures
+no good solution here
+add check submit button to leaderboard and ask students to use it
 
 \section*{Results}
-As the goals of a project naturally define evaluation criteria, I have evaluated my project on the basis of those goals.
+As the goals of a project naturally define evaluation criteria, I have evaluated my project on the basis of each those goals: decreasing the work to build each assignment within a semester and the instructor time allocated to assignment implementation, eliminate the inter-year assignment reconstruction, improve available student resources, and in doing so improve student and instructor satisfaction.
 
@@
 
+would like to not use separate files even if lots of the code is the same - complicates handout but simplifies code reuse and iteration
+
 Earlier assignments were built off of earlier versions of the infrastructure and will need to be ported to newer versions when they are reused: do next year

### 2018-05-06 paper.tex
Partway through implementation

@@
 This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and not null unless otherwise explicitly specified.
-Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html#unmodifiableList(java.util.List)}
+Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
 In order to preserve backwards compatibility, these features are not implemented by default.
@@
 
-now we can also have a better handout
-outline better handout
-* interface
-* dumb implementation
-* full copy of the above code
-comment on use of formatbase here
-comment on separate files for each assignment - why (simplify handout)
+Given all of the components described above, I have developed a considerably improved the assignment handout.
+Previously, the handout contained the strategy interface and a simple implementation strategy with a sample testing method for that implementation only.
+This semester, assignment handouts contained not just the strategy interface and simple implementation, but also a full copy of the above game round simulation, complete with amortization by many randomized trials, which simply prints the average score of each strategy.
+This testing code is not hard-coded to any implementation of the student strategy interface, but instead can be configured by the student modifying the configuration file to contain whatever strategies they want to simulate.
+For instance, given strategies \texttt{Student\_random.java} and \texttt{Student\_favorites.java} which apply to random schools and their favorite schools in the above college admissions simulation, all the student would need to do to simulate 10 submissions using the former strategy and 15 using the latter would be set the configuration file to ten lines of \texttt{random} and 15 lines of \texttt{favorites}, and then run \texttt{make test}.
+The handout will rewrite the simulation code to simulate those strategies using \texttt{formatBase.py} and then compile and run the simulation.
 
-but we wanted a grader. how to build grader from that?
-brief tangent to how to grade, not against peers
-introduce replacement-comparison grading
-* have some instructor strategies designed to perform well
-* substitute, for each student, a copy of each instructor strategy
-* grade based on how many instructor strategies the student's strategy did better than against the same pool
-* comment about incentive structures of this method: correct due to amortization (maximize your expectation to maximize your chance of beating unknown instructor thresholds.
-amortization means your outcome equals your expectation)
+The two most important components of each exercise are the handout code for the students and the autograder code for the instructors.
+However, in order to design the autograder, Professor Weinberg and I had to develop a well-specified, portable standard for grading strategy design exercises.
+A key constraint in the grading of these assignments is that the incentive for the students must be to try to maximize their own strategy's performance.
+Therefore, curving each student's grade based on the percentile of their strategy's performance is not acceptable: in this scenario, a student would be as happy to hurt their peers as to improve their own strategy.
+For instance, in an iterated prisoner's dilemma, if students are graded based on relative performance, then they are apathetic between both cooperating and both defecting.
+So there is no incentive under any circumstance to cooperate, even in the face of potentially irrational counterparties, and every student should always defect.
 
-issue with this: O(mn) time
-* can cut down to O(m) time by just adding each instructor strategy one by one and seeing how they do against the whole field.
-* assume that each individual student has negligible impact on that instructor's performance.
-* Comment as to whether this is a realistic assumption.
-* comment on incentives of this method - approximately correct as before
+One feasible grading strategy, given this constraint, would be to grade student performance without any curve at all.
+That is, in a simulation where the best possible performance is 5000 points, and the worst possible performance is 0 points, students would receive 3/5 on the assignment if they scored 3000 points on average.
+However, in this case, student grades can be negatively impacted by the decisions of their peers.
+For instance, in the prisoner's dilemma, for every student who always defected, every other student would have the cap on the maximum possible grade they could receive lowered.
+Students' grades would be dominated not by the performance of their own strategy but by the decisions of their peers.
+Course staff including Professor Weinberg agreed that this is unacceptable.
 
-back to buidling the grader
-manually write the list of grader strategies
-make a new method very similar to one each trials: with extra trials
-lookup table: how many instructor strategies beat -> score
-didn't need to change the trial at all
-so that doesn't need to be changed when makign a new assignment
-we can now grade every assignment
+``Replacement-comparison grading'', the grading rubric used in the course, was developed by Professor Weinberg and myself as a dependency of my work on this project, created to satisfy the need for an incentive-correct grading rubric which could be implemented in an autograder.
+It is based on the following intuition: the performance of a student strategy $S_i$ among strategies $S_1 \ldots S_n$, pro-rated based on the potential best and worst possible performances by any strategy in the simulation, can be captured by comparing the score $x_i$ of $S_i$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$ to the scores $y_{i,1} \ldots y_{i,m}$ of a predetermined menagerie of $m$ instructor strategies $I_1 \ldots I_m$, where each $y_{i,j}$ in $y_{i,1} \ldots y_{i,m}$ is the score of $I_j$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$.
+That is, to grade a given student's strategies in a room with their peers, substitute each instructor in their place while making no other changes to the room, and measure whether the student does better or worse than that instructor would have in their place.
+Students whose strategies outperform all instructor-designed strategies have done better than the instructors would have at the assignment, and receive the best grades.
+Some instructor-designed strategies are intentionally imperfect or misguided, in order to differentiate between less ideal student-designed strategies.
+
+The grading strategy described above has the correct incentives: each student will attempt to maximize their chance of beating each instructor threshold.
+Since the instructor strategies used for grading are not revealed, and the pool of other student submissions is unpredictable, the distribution of instructor thresholds approaches uniform, and students will attempt to beat as much of the real interval of the score range as possible, which is the same behavior as maximizing expectation.
+Additionally, by amortizing student performance over many randomized trials, for instance by reassigning student and university preference orderings in the college applications game independently between trials, the law of large numbers guarantees to students that their grade represents their expected performance without uncertainty based on variance between trials.
+So students are not incentivized to play a lower-expectation strategy in order to increase their variance, or any other higher-order moment of their strategy.
+The only concern would be if a student `played mean' to hurt instructor scores, but since instructor scores for a given student are calculated without the play of this student, students could not improve their own grade by doing so.
+
+Though the above strategy achieves all the correctness requirements, it has a fatal flaw: when there are $n$ student strategies and $m$ instructor strategies, and a trial with $n$ strategies takes $t(n)$ time, this grading metric takes $O(m \cdot n \cdot t(n))$ time.
+After approval from Professor Weinberg, I implemented a simple optimization to bring down the time requirement to $O((m+1) \cdot t(n+1))$ time.\footnote{So long as $t$ grows slower than $n!
+$, this is a performance improvement; for practical reasons, all simulations used in this course take polynomial time in the number of students.}
+The modified replacement-comparison grading scheme measures student scores $x_1 \ldots x_n$ for all students $S_1 \ldots S_n$ amortized across many trials, then for each instructor strategies $I_j$ among $I_1 \ldots I_m$, measures their score $y_j$ against all of $S_1 \ldots S_n$.
+That is, instructor strategies are assigned scores based on their performance against all the students, and student strategies are assigned scores based on their performance against all the other students.
+The only difference between the initial and modified replacement-comparison schemes is that each student can have some small impact on the thresholds used to grade them, not just their peers.
+Thus, if a student `played mean' and hurt instructor scores, they might perform better.
+However, among a course of over 100 students, the impact of any individual student on any instructor's score is assumed to be negligible.
+The strength of this assumption needs to be verified during the development of an assignment.
+
+The goal of this project is not to build a handout, or an autograder, but to build a framework in which the development of the grader as described above requires no modification of assignment-specific code.
+Consider the components of the simulation handout:
+\begin{itemize}
+\item \texttt{runTrial} method which takes a list of strategies and simulates their behaviors in e.g.\ a college admissions simulation
+\item data processing methods, e.g.\ \texttt{oneEachTrial} which builds a list containing each configuration-specified strategy once\footnote{see figure above} and \texttt{oneEachTrials} (not shown above) which runs \texttt{oneEachTrial} a large number of times and averages the results
+\item postprocessing methods, e.g.\ to output a CSV file containing student names and their average performance in the simulation
+\end{itemize}
+Only the first of these contains assignment-specific code.
+In order to implement replacement-comparison grading, I implemented the following methods:
+\begin{itemize}
+\item two new data processing methods, \texttt{withExtraTrial} which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter\footnote{see figure above}, and a corresponding method \texttt{withExtraTrials} which averages the above.
+These are very similar to the existing data processing methods.
+\item A new postprocessing method that computes grades for each student given how many instructor strategies each student strategy beat and a lookup table.\footnote{make into figure/appendix}
+\end{itemize}
+\begin{verbatim}
+    public static void writeGrades () {
+        final int numTrials = 1;
+        //R netids[{0}] = "{netID}";//
+        // defaults as specified in assignment handout PDF
+        final double S = 100, T = 100, W = 10;
+        // Compute x_i
+        double[] oneEachTrials = oneEachTrials(100, S, T, W);
+
+        // Instructor strategies
+        List<Class<? extends Student>> ourStrats =
+            new ArrayList<Class<? extends Student>>();
+        ourStrats.add(Student_REDACTED.class);
+        // a total of twelve such lines like the above line
+        double[] winsToPoints = new double[]{
+            0, 0.5, 1.0, 1.2, 1.5, 1.8, 2, 3, 3.5, 4.0, 4.5, 4.8, 5
+        };
+        // Compute \sum_j \delta_{x_i > y_j} for all i
+        int[] wins = new int[N];
+        for (Class<? extends Student> strat : ourStrats) {
+            double[] res = withExtraTrials(strat, numTrials, S, T, W);
+            for (int i = 0; i < N; ++i) {
+                if (res[i] > res[N]) {
+                    ++wins[i];
+                }
+            }
+        }
+        // Output grades as csv
+        System.out.println("netID,points");
+        for (int i = 0; i < N; ++i) {
+            System.out.println(netids[i] + "," + Double.toString(oneEachTrials[i])
+                               + "," + Double.toString(winsToPoints[wins[i]]));
+        }
+    }
+\end{verbatim}
+Given only these two changes, the handout code has been transformed into an autograder.
+Additionally, neither of these changes required alteration of the \texttt{runTrial} method, so minimal additional work (only filling in the instructor strategy names and scoring rubric) is necessary for grading an assignment once the handout has been made.
+
+so now we have a framework which makes it easy to build new assignments
+what really changes?
+build ultimatum
+\footnote{TODO UML outline for reference}
 
@@
 
-so now we have a framework which makes it easy to build new assignments
-what really changes?
-build ultimatum
+As currently implemented, each assignment was distributed as a standalone zip file through the course website.
+Thus, even though very little code was changed between the two assignments described above,
+more convenient in cases where minor grader tweaks are sadly necessary
+comment on separate files for each assignment - why (simplify handout)
 

### 2018-05-07 paper.tex
Implementation

@@
 
-so now we have a framework which makes it easy to build new assignments
-what really changes?
-build ultimatum
-\footnote{TODO UML outline for reference}
+In summary, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that postprocess the results of those trials to provide low-latency feedback or for autograding, and hooking all of the above together a \texttt{Makefile} to configure, compile, and run the assignment simulation.
+\footnote{TODO redraw using Powerpoint}
+\footnote{TODO add formatBase.py config csv}
 
-catch: sometimes we want to simulate multiple parameter settings for student code
-involves changing the main method a bit
-not much change
+\begin{figure}[hbt]
+\centering
+\includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
+\caption{This is a gray image.}\label{fig:gray}
+\end{figure}
+
+In addition to easily altering an assignment handout into an autograder, my framework also makes it easy to build new assignments.
+To adapt the college admissions exercise described above into the elections simulation of the second problem set of COS 445 this spring, only a few changes were necessary.
+The written assignment specification describes a new interface, so a whole new interface file was necessary.
+Of course, all the implementations of this interface were also written from scratch for the new assignment, all of which are fairly concise but express assignment-specific strategies.
+And finally, the \texttt{runTrial} method of the simulator had to be rewritten to simulate an election instead of college admissions, and some file names had to be changed.
+No semantic changes were necessary to the data processing or postprocessing methods for either the handout or application.
 
 As currently implemented, each assignment was distributed as a standalone zip file through the course website.
-Thus, even though very little code was changed between the two assignments described above,
-more convenient in cases where minor grader tweaks are sadly necessary
-comment on separate files for each assignment - why (simplify handout)
+Thus, even though significant code was shared between the two assignments described above, they were distributed as separate files.
+While further modularization would allow assignment-specific code describing how to simulate a game round to be separated out from code which changes within, but not between, assignments, I determined during assignment development that maintaining separate codebases for each assignment has significant advantages.
+Some simulation parameters, such as the budget constraint or number of auctioned items in an auction, the variance of student preferences in an admissions simulation, or the number of polling rounds in an election, vary between assignments.
+Often, strategies are evaluated based on their performance relative to baseline instructor strategies in several different regimes of simulation parameters.
+This will involve tweaks to the grader code outside of the scope described above.
+While these changes are minimal and necessary, keeping details of grading separate between assignments proved useful in the real world.
 
-we also have a framework to build new tools
-let's build new tools
-what shoudl we build?
-what problems to address?
-ease of testing
-``Works On My Machine''
-getting a better idea about how a strategy would perform against more realistic collection of peers
+Thus far, I have illustrated the strengths of my project at performing tasks which were envisioned from the outset.
+The strength of modular implementation comes also from the ability to adapt to changing demands easily in real time.
+In this way, I was able to extend my framework throughout the semester in order to address my needs as a course assistant to remedy issues with the strategy design exercises.
+As shown below,\footnote{results section ref here} the handout code enabled students to verify that their code compiled and ran.
+However, several students submitted non-functioning strategies due to environmental differences, demonstrating the classic issue, ``Works On My Machine''.
 
-dropbox checksubmit
-learned how cs dropbox works
-a little bash + make to copy in the student handout, detect and write a config file to run their code
-show script + makefile
-show an output
+Other computer science courses at Princeton employ an online tool in the CS DropBox called ``Check Submit''.
+This tool allows instructors to specify tests to be run on department-configured machines using student code, and students to evaluate the performance of their submission against these tests without the concern that the software environment on their machine might not be compatible.
+I enabled ``Check Submit'' for COS 445 strategy design exercises as a part of this work by developing simple Bash script and Makefile which adapts my assignment framework to this new setting.
+All the script has to do is copy in the assignment handout from a predefined location into the student submission folder, detect the student submission name, and write the \texttt{formatBase.py} configuration file to run their submission.
+Now, without any modification of the assignment code, every strategy design exercise automatically has DropBox ``Check Submit'' functionality possible!
 
-leaderboard
-new tools: cycles cron
-simple to copy in all submissions, detect and write config file, run code, post it to website
-discuss issues
-student code breaking it
-harden the tester (try catch around each student with selfless behavior)
-student code causing compile failures
-no good solution here
-add check submit button to leaderboard and ask students to use it
+This confirms to students that their strategy will not be incompatible with the grading environment, improving student satisfaction with the course.
+However, students would still benefit from more realistic testing.
+Thus, I developed a leaderboard so students could better understand how a strategy would perform against more realistic collection of peer strategies.
+First, I initialized a new DropBox assignment for students to submit strategies to the leaderboard, which need not be their final assignment submission.
+I implemented the leaderboard by writing a simple Bash script which scrapes all student submissions from the DropBox, automatically writes the configuration file to run every students' submission together, and runs the simulation provided in the student handout as above.
+Because the simulation output is an easy-to-parse table, I can automatically reformat it into an HTML table and place this in a web page accessible through the department web servers.
+The script to update the leaderboard runs through a cronjob at a customizable interval.
+
+While this leaderboard provides additional feedback, there are unavoidable issues when students submit broken code.
+Since all student submissions are run together, one non-compiling or exception-throwing submission disables the leaderboard for all students.
+I worked around this issue by disabling assertions, which were used in \texttt{runTrial} to automatically halt simulation whenever a student submission performed behavior in violation of the assignment specification.
+Then, the code automatically fell back to silently overriding illegal values from student strategies with sane but selfless defaults, and the leaderboard is correctly generated even when some student submissions are faulty.
+Some student code also caused compilation failures, which are more difficult to work around.
+We enabled the check submit button to leaderboard so that students could check their leaderboard strategies would compile in the department environment, and this mostly resolved the issue.
+
+The full implementation available at the course GitHub site.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s18 requires invite}
 

### 2018-05-07 paper.tex
Revisions to paper through Implementation, also wrote Acknowledgements and Ethics

@@
 \documentclass[pageno]{jpaper}
-
+%%% Local Variables:
+%%% TeX-command-extra-options: "-shell-escape"
+%%% End:
 \newcommand{\Semester}{Spring}
@@
 \newcommand{\quotes}[1]{``#1''}
-\makeatletter
-\def\verbatim@font{\linespread{1}\normalfont\ttfamily}
-\makeatother
+
+\usepackage{minted}
+\setminted{baselinestretch=1}
+
 \clubpenalty9998
@@
 \begin{abstract}
-  Student interest in Princeton's undergraduate course in algorithmic game theory, ``Economics and Computing'' (COS 445), has grown rapidly in recent years.
+  Student interest in ``Economics and Computing'', Princeton's undergraduate computer science course in algorithmic game theory, has grown rapidly in recent years.
   This course employs small simulations to develop students' ability to use theoretical tools to analyze more real-world situations.
-  These strategy design exercises require considerably more software infrastructure than would a usual theoretical problem set, including handout code for student self-evaluation and software autograders.
+  These strategy design exercises require considerably more software infrastructure than a usual theoretical problem set would, including handout code for student self-evaluation and software auto-graders.
   While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly structured assignments and evaluating student submissions in the context of each other.
@@
 \section*{Introduction}
-My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course.
-The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally, within healthy incentive structures where students do not try to hurt each others’ performance.
-Each past offering of the course has rebuilt these assignments from scratch, and all associated instructor tooling, resulting in unnecessarily high allocation of instructor time to grading.
+My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course, COS 445 ``Economics and Computing''.
+The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally within a healthy incentive structure where students do not try to hurt each others’ performance.
+Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
 Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
-In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for the students, I develop an extensible framework to improve these strategy design exercises.
+In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for students, I developed an extensible framework to improve these strategy design exercises.
 
-Four Princeton University departments offer courses in game theory: economics, politics, mathematics, and computer science.
+Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
 While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
-For instance, in the computer science department, COS 445, ``Economics and Computing'', places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
-This is represented in the course topics, which focus on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
-It is also represented in the design of the problem sets, which contain, in addition to traditional proof-based exercises, programming-based exercises which connect course topics to prerequesite computer science skills.
+For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
+The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
+It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
 These programming-based exercises take a common form.
@@
 Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
-A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java iterface}, in which two players must collaborate to receive the best outcome, but are each incentivized to defect, which results in a less preferred outcome, and have acecss to the other player's play history when making their own decision.
-While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including, from semester to semester, a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
+A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java interface}, in which two players must collaborate to receive the best outcome, but are each incentivized to defect, which results in a less preferred outcome, and have access to the other player's previous decisions when making their own decision.
+While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
 These examples are not exhaustive, but illustrate the variety of course topics with potential for translation to iterated games.
 
-Students then craft strategies to play the specified game, based on their own analyses of the game's equilbirium, and based on their own priors over the strategies which will be designed by their peers.
+Students then craft strategies to play the specified game, based on their own analyses of the game's equilibrium and on which strategies they expect their peers to play.
 These strategies are evaluated on both on their design quality and on their empirical performance.
-While design quality is evaluated on a purely individual basis, empirical performance is measured by simulating the play of the collection of submitted student strategies.
-For instance, for the iterated prisoner's dilemma, every student strategy plays one full game (consisting of many iterations of the prisoner's dilemma) against each other strategy, and strategies are scored based off the average payoff they achieved.
-For the search advertisement game, all the student strategies are concurrently asked to bid on the same search terms, and are scored based on their revenue from ad clicks (where each bidder knows the click-through rate for a term prior to bidding on that term) less their expenditures on advertising.
-To create a more realistic simulation, students are graded solely the performance of their own strategy, not on a curve of the performance of their peers.
+While design quality is evaluated on a purely individual basis, empirical performance is measured by simulating the play of the collection of submitted student strategies against each other.
+For instance, for the iterated prisoner's dilemma, every student strategy plays one `full' game, consisting of many iterations of the prisoner's dilemma, against each other student strategy.
+Strategies are scored based off the average payoff they achieve.
+For the search advertisement game, all the student strategies are concurrently asked to bid on the same search terms.
+They are scored based on their revenue from ad clicks less their expenditures on advertising, and each bidder knows the click-through rate for a term prior to bidding on that term.
+To create a more realistic simulation, students are graded solely on the performance of their own strategy, not on a curve of the performance of their peers.
 That is, student grades on these strategy design exercises are not zero-sum.
 
-While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demanded considerable instructor resources be dedicated to building and grading software resoruces, which have historically been significantly rebuilt for each assignment.
+While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand considerable instructor resources be dedicated to building and grading software resources, which have historically been significantly rebuilt for each assignment.
 Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
-Due to the limited tooling provided in past semesters for students to evaluate their submissions, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
+Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
 
-The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
-This was accomplished by designing a reuasble framework which embodies the commonality between strategy design exercises, allowing instructors creating new exercises to change only the necessary, assignment-specific details, and which will include more advanced automated grading tools than previously existed for the course.
+%TODO: move the above into the body / approach and the above as the introduction
+The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
+This was accomplished by designing a reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
 Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
 
-Through this work, I aim to improve the quality of computer science theory education, from the perspectives of both the students and faculty associated with COS 445.
-Quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
+Through this work, I aim to improve the quality of computer science theory education from the perspectives of both the students and faculty associated with COS 445.
+Quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
 
@@
 This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
-In one problem set, students developed and implemented strategies for three different strategy design exercises, related to three different classical games: Prisoner's Dilemma, Centipede, and Ultimatum.
+In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different classical games: Prisoner's Dilemma, Centipede, and Ultimatum.
 In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid.
@@
 Both problem sets were implemented and graded by Cyril Zhang\footnote{https://github.com/cyrilzhang}, a graduate student TA for the course.
-Cyril developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
-However, this existing implementation of grader software for strategy design assignments is not modular and has to be completely rewritten for each assignment, and was designed for grader use only.
-The student interfaces were documented, but the grader software was not documented for future re-use.
-Additionally, some of the scripts and notebooks used by Cyril were not preserved and were not accessible as resources.
-Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Cyril's code.
+Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
+However, his implementation of software for strategy design assignments was intended for grader use only.
+It is not modular and has to be completely rewritten for each assignment.
+The student interfaces were documented, but the grader software was not documented for future use.
+Additionally, some of the scripts and notebooks used by Zhang were not preserved and were not accessible as resources.
+Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Zhang's code.
 
-Previous to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
-Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code respositories used by the course staff.
+Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
+Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
 In both semesters, Yonatan Naamad\footnote{https://github.com/ynaamad/} was responsible for software development.
@@
 The only resources available from Fall 2012 were collected from the course Google Code repository.\footnote{https://code.google.com/archive/p/cos445-scripts/}
-This repository contains incomplete Python skeleton code for a basic tournament.
-This was uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but was not reused.
+This repository contains incomplete Python skeleton code for a basic tournament of an unspecified game.
+I uploaded this code to the current course repository\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.
 
@@
 Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
-The Java code consisted of student handouts of interfaces and some testing code, but the testing code was not designed to be automated for grading and was not modular: it tested manually-enterred strategies against each other and assignment-specific details (e.g.\ game structure and payoffs) were integrated within the simulation code.
+The Java code was the student handout, which contained strategy interfaces and some testing code.
+The testing code was not designed to be automated for grading and was not modular.
+It tested manually-entered strategies against each other, and assignment-specific details, such as game structure and payoffs, were integrated within the simulation code.
 As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
@@
 Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
-However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.
+However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke,\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.
 
 Harvard's Computer Science 136, ``Economics and Computation'',\footnote{https://beta.blogs.harvard.edu/k108875/assignments/} assigns two programming problem sets.
-The first requires implementation of a peer-to-peer filesharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
+The first requires implementation of a peer-to-peer file sharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
 However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
@@
 This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
-However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and the implementation is in Python.
+However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and that the implementation is in Python.
 While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
-Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445 at Princeton.
+Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445.
 
@@
 Such resources are useful in the general case of developing new programming-based assignments, but no such resources replicate the behavior implemented in this project.
-Most autograding systems are designed with an assumption that student submission are graded in a sandbox, isolated from other student submissions.
-Such systems are not applicable to this project, since the strategy design exercises involve evaluation of student strategy performance in a common environment.
-However, existing resources for assignment submission and student feedback in use by Princeton are used in this assignment.
-I integrated some CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and modelled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
-Generally, however, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.
+Most auto-grading systems are designed with an assumption that each student submission is graded in isolation from other student submissions.
+Such systems are not applicable to this project since the strategy design exercises involve evaluation of student strategy performance in a common environment.
+Though existing automatic grading systems cannot replicate the full extend of this work, I integrate existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
+I integrated CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
+Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.
 
 \section*{Approach}
-Cyril Zhang completed the TA requirement for the PhD program last fall, so at the start of this semester it was unclear who among the graduate and undergraduate course staff would be responsible for maintaining these assignments.
-Thus, the course needed not just long-term work to improve student and instructor resources, but also short-term work to maintain and debug the same resources.
-These harmonizing requirement suggest that the product should consist of one extensible implementation of all the reusable components for software design exercises, developed iteratively in conjunction with its usage in the course.
+Cyril Zhang completed the TA requirement for the PhD program last fall, so at the start of this semester it was unclear who among the graduate and undergraduate course staff would be responsible for maintaining the COS 445 strategy design exercises.
+Therefore, the course needed not just long-term work to improve student and instructor resources, but also short-term work to maintain and debug the same resources.
+These coinciding requirements inspired me to design one extensible implementation of all the reusable components for software design exercises, and to develop the project iteratively in conjunction with its usage in the course.
 This software would naturally grow throughout development as demanded by the needs of the course, and the final product will naturally lower-bound the maximum degree of automation and modularity possible.
 
-Before the first problem set of the course was assigned in this semester, Matt and I designed and I implemented a handout interface and tools to allow students to test their strategies against each other.
+Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
 The game simulates college admissions using stable matchings.
-While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design covered in previous courses.\footnote{Kernighan and Pike chapter 4}
-I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which amortized results from multiple randomized trials, and from agglomerated these results to output performance statistics for students.
-Thus, when it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trails changed from college admissions to elections.
+While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.\footnote{Kernighan and Pike chapter 4}
+I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.
+When it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trials changed from college admissions to elections.
 Additionally, when it came time to grade the problem set, I was able to modify only the post-processing step to compute grades.
-Thus, creating a new assignment requires constant work in the number of framework extensions, and creating a new framework extension requires constant work in the number of assignments.
-
+Thus, creating a new assignment required constant work in the number of framework extensions, and creating a new framework extension requires constant work in the number of assignments.
+% TODO: maybe put stuff from earlier here?
 The result of this process duplicates significant functionality from last year's assignments.
-However, because of conscious design decisions to factor our repeated code from assignment implementations, it accomplishes what previous implementations had not.
+However, because of conscious design decisions to factor out repeated code from assignment implementations, it accomplishes what previous implementations had not.
 It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
 Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
-And, it will be reusable, both for the same assignments in future years, and for new strategy design exercises implemented by future course staff with lower overhead.
+It will be reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
 
-In order to increase the reusability, I elected to store it in a University-owned private GitHub repository.
-This ensures that, even after I have graduated, future course staff will have access to the project.
-Additionally, I documented the repository structure and each program's role in the repository, as documented later in this document.
+In order to increase the reusability, I elected to store it in a University-owned private GitHub repository and documented the repository structure and contents.
+This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.
 
 \section*{Implementation}
+% TODO: signposting
 The first key decision in the implementation of these programming assignments was language selection.
@@
 Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
-Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parametrized on user-input strategy names.
-Unfortunately, COS 445 does not have Python experience as a course prerequisite, only Java experience.
-Additionally, survey data from other course surveys suggests that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python.\footnote{COS 333 survey data}
+Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parameterized on user-input strategy names.
+Unfortunately, COS 445 only prerequisites Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
+Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{COS 333 survey data}
 
-Thus, the whole system under consideration is constrained: it must support student strategy implementations in Java.
-Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignments as possible in Java, with limited usage of scripting languages such as make, Python, and bash.
-These scripting languages were used where Java would not suffice and only for tasks for which implementation details were irrelevant to student assignment comprehension.
+Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
+These scripting languages were used only where Java would not suffice and only where implementation details were irrelevant to student assignment comprehension.
 
 Java also offers convenience to assignment designers by enforcing an object-oriented design pattern.
-This allows instructors to communicate an assignment specification formally through a well-documented interface.
-Furthermore, by constructing new instances of the student implementations between game rounds, instructors can programatically enforce that students do not employ learning strategies outside the parameters of the assignment.\footnote{This requires that instructors forbid the usage of static variables, but it is trivial to verify compliance with this requirement.}
+This allows instructors to communicate assignment specifications formally through a well-documented interface.
+Furthermore, by constructing new instances of student implementations between game rounds, instructors can programatically enforce that students do not employ learning strategies outside the parameters of the assignment.\footnote{This requires that instructors forbid the usage of static variables, but it is trivial to verify compliance with this requirement.}
 
@@
 For instance, Java objects used as function parameters are passed by mutable, nullable reference.
-This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and not null unless otherwise explicitly specified.
+This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and nonnull unless otherwise explicitly specified.
 Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
@@
 Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
-However, I have not included NotNull annotations because they are not taught in the prerequesite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
+However, I have not included NotNull annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
 In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}
 
-In order to design my framework, I reviewed unmodularized code from a past strategy design exercise, the Spring 2017 auctions exercise.
-This is the only assignment to which I had access to the full implementation of the student handout (having taken the course) and the grader code (preserved by Professor Weinberg).
-The first piece of the assignment to be implemented, after the game design is complete, is the student interface:\footnote{TODO: make this code a figure}
-\begin{verbatim}
+\subsection*{Handout Implementation}
+In order to design my framework, I reviewed non-modularized code from the Spring 2017 auctions exercise.
+This is the only assignment for which I had access to both the student handout and the grader code.
+After the game design is complete, the first piece of the assignment to be implemented is the student interface:\footnote{TODO:\ make this code a figure}
+\begin{minted}{java}
 import java.util.List;
@@
 }
-\end{verbatim}
-This interface describes what students' strategies must do: they must, each day, bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results''), and they value the word being auctioned each day at a different value.
-The strategy also has access the winning bids for each of the ten sponsored results from each past day, and knows if it won any auctions itself, and if so how much it paid.
+\end{minted}
+This interface describes the necessary functions of a student strategy.
+Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results''), and they assign different values to words auctioned on different days.
+The strategy also has access the winning bids for each of the ten sponsored results from each past day and which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
 This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
 These constants are not documented in the interface as designed, only in the assignment specification.
-The instructors distribute a simple sample student implementation, in this case the truthful bidder.
-Cyril also implemented a program used to grade the student-submitted strategies.
-This program had two methods: \texttt{main} and \texttt{trial}.
+The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
+Zhang also implemented a program used to grade the student-submitted strategies, which consisted of two methods: \texttt{main} and \texttt{trial}.
 The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
@@
 Having reviewed a former assignment, I implemented the first assignment handout for the course this semester: the college admissions simulation described previously.
-In doing so, I made several implementation decisions in order to facilitate future reconfiguration of the game being played and of the postprocessing of the tournament results which are representative of design decisions made throughout the assignment.
-In every assignment, the tournament simulation portion (instructor-written code) is broken up into game rounds, result processing and amortization, and further postprocessing, such as grade assignment and output formatting.
-The divide between game rounds and code which processes game results was present in Cyril's auction code, as the separation between the \texttt{trial} and \texttt{main} methods.
+In doing so, I made several implementation decisions in order to facilitate future reconfiguration of both the game being played and the post-processing of tournament results, which are representative of design decisions made throughout the assignment.
+In every assignment, the tournament simulation portion (instructor-written code) is broken up into game rounds, result processing and amortization, and further post-processing, such as grade assignment and output formatting.
+The divide between game rounds and code which processes game results was present in Zhang's auction code, as the separation between the \texttt{trial} and \texttt{main} methods.
 However, this prior work did minimal amortization and no advanced output formatting, and had no separation between them.
-While the handout code written for the first assignment did minimal postprocessing, this distinction was quite useful when later developing the autograder and additional extensions.
+While the handout code written for the first assignment did minimal post-processing, this distinction was quite useful when later developing the auto-grader and additional extensions.
 
 During the development of this handout, however, the statically-typed nature of Java raised some difficulty.
-Cyril's code had student submission names hardcoded into complex expressions, as though they had been copied in from a manually-written list formatted using sed.
-In the context of developing a handout to allow students to test multiple strategies of their own design, I determined requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
-Additionally, graders desire functionality to configure the list of strategies to be evaluated at grading time, without having to manually list out all the student strategy names, and to easily modify this list to identify and diagnose misbehaving student strategies.
+Zhang's grader code had student submission names hardcoded into complex expressions, as though they had been copied in from a manually-written list formatted using \texttt{sed}.
+In the context of developing a handout to allow students to test multiple strategies of their own design, I determined that requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
+Additionally, graders desire functionality to configure the list of evaluated strategies without having to manually list out all the student strategy names and to modify this list repeatedly to identify and diagnose misbehaving student strategies.
 Since Java is not able to type-check user-input strategy names, I determined that the most effective workaround for this issue would be to automatically rewrite the Java code before compile-time.
@@
 For this purpose, I developed a simple Python script capable of rewriting arbitrary template plaintext files using a CSV file.
-This script, \texttt{formatBase.py}, builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
-Then, it rewrites its input by finding lines which start with \texttt{//R} and end with \texttt{//}, and replaces each such line with, for each row of the CSV, the line rewritten by replacing each curly-enclosed key with the corresponding value from that row.
+This script, \texttt{formatBase.py},\footnote{TODO: appendix this} builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
+In its input, it identifies lines which start with \texttt{//R} and end with \texttt{//}.
+For each such line in its input, it outputs multiple lines, each corresponding to the input line rewritten using a distinct row of the CSV by replacing each curly-enclosed key with the corresponding value.
 It also rewrites the key \texttt{0} with the row number from the configuration table.
@@
 \footnote{use figure}
-\begin{verbatim}
+\begin{minted}{java}
+    // S, T, W are simulation parameters documented in the student interface
     public static int[] oneEachTrial(double S, double T, double W)
@@
     }
-\end{verbatim}
-In the above code from the college applications simulator, \texttt{S}, \texttt{T}, and \texttt{W} are configuration parameters for the simulation which were documented in the student interface.
-For contrast, the following method also instantiates an instance of an instructor-provided strategy using reflection.
-This illustrates potential variation in data collection code as enabled by my modular design, and is used in the autograder described below.
+\end{minted}
+My modular design allows for data collection code to vary without additional overhead.
+The following method instantiates an instance of an instructor-provided strategy using reflection, in addition to the strategies specified in the configuration file.
+This method is useful for grading assignments.
 \footnote{todo: figure}
-\begin{verbatim}
+\begin{minted}{java}
     public static <Student_T extends Student> int[] withExtraTrial(
@@
     }
-\end{verbatim}
+\end{minted}
 
@@
 This semester, assignment handouts contained not just the strategy interface and simple implementation, but also a full copy of the above game round simulation, complete with amortization by many randomized trials, which simply prints the average score of each strategy.
-This testing code is not hard-coded to any implementation of the student strategy interface, but instead can be configured by the student modifying the configuration file to contain whatever strategies they want to simulate.
+While working on the assignment, students can reconfigure the testing code easily by modifying the configuration file to contain whatever strategies they want to simulate.
 For instance, given strategies \texttt{Student\_random.java} and \texttt{Student\_favorites.java} which apply to random schools and their favorite schools in the above college admissions simulation, all the student would need to do to simulate 10 submissions using the former strategy and 15 using the latter would be set the configuration file to ten lines of \texttt{random} and 15 lines of \texttt{favorites}, and then run \texttt{make test}.
-The handout will rewrite the simulation code to simulate those strategies using \texttt{formatBase.py} and then compile and run the simulation.
+Whereas, last year, each student would have had to manually write simulation code to run the exact collection of strategies they wanted to simulate, the new handout will automatically rewrite the simulation code to simulate those strategies using \texttt{formatBase.py} and then compile and run the simulation with no additional overhead.
 
-The two most important components of each exercise are the handout code for the students and the autograder code for the instructors.
-However, in order to design the autograder, Professor Weinberg and I had to develop a well-specified, portable standard for grading strategy design exercises.
+\subsection*{Auto-Grader Design}
+The two most important components of each exercise are the handout code for the students and the auto-grader code for the instructors.
+However, in order to design the auto-grader, Professor Weinberg and I had to develop a well-specified, portable standard for grading strategy design exercises.
 A key constraint in the grading of these assignments is that the incentive for the students must be to try to maximize their own strategy's performance.
-Therefore, curving each student's grade based on the percentile of their strategy's performance is not acceptable: in this scenario, a student would be as happy to hurt their peers as to improve their own strategy.
+Therefore, curving each student's grade based on the percentile of their strategy's performance is not acceptable.
+In this scenario, a student would be as happy to hurt their peers as to improve their own strategy.
 For instance, in an iterated prisoner's dilemma, if students are graded based on relative performance, then they are apathetic between both cooperating and both defecting.
@@
 Students' grades would be dominated not by the performance of their own strategy but by the decisions of their peers.
-Course staff including Professor Weinberg agreed that this is unacceptable.
+Course staff, including Professor Weinberg, agreed that this is unacceptable.
 
-``Replacement-comparison grading'', the grading rubric used in the course, was developed by Professor Weinberg and myself as a dependency of my work on this project, created to satisfy the need for an incentive-correct grading rubric which could be implemented in an autograder.
-It is based on the following intuition: the performance of a student strategy $S_i$ among strategies $S_1 \ldots S_n$, pro-rated based on the potential best and worst possible performances by any strategy in the simulation, can be captured by comparing the score $x_i$ of $S_i$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$ to the scores $y_{i,1} \ldots y_{i,m}$ of a predetermined menagerie of $m$ instructor strategies $I_1 \ldots I_m$, where each $y_{i,j}$ in $y_{i,1} \ldots y_{i,m}$ is the score of $I_j$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$.
-That is, to grade a given student's strategies in a room with their peers, substitute each instructor in their place while making no other changes to the room, and measure whether the student does better or worse than that instructor would have in their place.
+``Replacement-comparison grading'', the grading rubric used in the course, was developed by Professor Weinberg and myself as a dependency of my work on this project, and satisfies the need for an incentive-correct grading rubric which could be implemented in an auto-grader.
+It is based on the following intuition: to grade a given student's strategies in a room with their peers, substitute each instructor in their place while making no other changes to the room, and measure whether the student does better or worse than that instructor would have in their place.
+The performance of a student strategy $S_i$ among strategies $S_1 \ldots S_n$, pro-rated based on the potential best and worst possible performances by any strategy in the simulation, can be captured by comparing the score $x_i$ of $S_i$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$ to the scores $y_{i,1} \ldots y_{i,m}$ of a predetermined menagerie of $m$ instructor strategies $I_1 \ldots I_m$, where each $y_{i,j}$ in $y_{i,1} \ldots y_{i,m}$ is the score of $I_j$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$.
 Students whose strategies outperform all instructor-designed strategies have done better than the instructors would have at the assignment, and receive the best grades.
@@
 
-The grading strategy described above has the correct incentives: each student will attempt to maximize their chance of beating each instructor threshold.
-Since the instructor strategies used for grading are not revealed, and the pool of other student submissions is unpredictable, the distribution of instructor thresholds approaches uniform, and students will attempt to beat as much of the real interval of the score range as possible, which is the same behavior as maximizing expectation.
-Additionally, by amortizing student performance over many randomized trials, for instance by reassigning student and university preference orderings in the college applications game independently between trials, the law of large numbers guarantees to students that their grade represents their expected performance without uncertainty based on variance between trials.
-So students are not incentivized to play a lower-expectation strategy in order to increase their variance, or any other higher-order moment of their strategy.
-The only concern would be if a student `played mean' to hurt instructor scores, but since instructor scores for a given student are calculated without the play of this student, students could not improve their own grade by doing so.
+This grading strategy has the correct incentives: each student will only work to maximize their chance of beating each instructor threshold, and not to sabotage their peers' performance.
+Since the instructor strategies used for grading are not revealed and the pool of other student submissions is unpredictable, the distribution of instructor thresholds approaches uniform, and students will attempt to beat as much of the real interval of the score range as possible, producing the same behavior as students maximizing expectation.
+Additionally, by amortizing student performance over many randomized trials --- for instance by reassigning student and university preference orderings in the college applications game independently between trials --- the law of large numbers guarantees to students that their grade represents their expected performance without uncertainty based on variance between trials.
+Thus, students are not incentivized to play a lower-expectation strategy in order to increase their variance.\footnote{The same analysis holds for all higher moments of their strategy.}
+This system is not vulnerable to students attempting to sabotage instructor scores for their own benefit, since instructor scores for a given student are calculated without the play of this student.
 
@@
 The modified replacement-comparison grading scheme measures student scores $x_1 \ldots x_n$ for all students $S_1 \ldots S_n$ amortized across many trials, then for each instructor strategies $I_j$ among $I_1 \ldots I_m$, measures their score $y_j$ against all of $S_1 \ldots S_n$.
-That is, instructor strategies are assigned scores based on their performance against all the students, and student strategies are assigned scores based on their performance against all the other students.
-The only difference between the initial and modified replacement-comparison schemes is that each student can have some small impact on the thresholds used to grade them, not just their peers.
-Thus, if a student `played mean' and hurt instructor scores, they might perform better.
-However, among a course of over 100 students, the impact of any individual student on any instructor's score is assumed to be negligible.
-The strength of this assumption needs to be verified during the development of an assignment.
+That is to say, instructor strategies are assigned scores based on their performance against all the students, while student strategies are assigned scores based on their performance against all the other students.
 
-The goal of this project is not to build a handout, or an autograder, but to build a framework in which the development of the grader as described above requires no modification of assignment-specific code.
+The only difference between the initial and modified replacement-comparison schemes is that each student can have some small impact on the thresholds used to grade themselves, not just their peers.
+As an unfortunate consequence of this simplification, if a student was able to hurt instructor scores, they might perform better.
+However, since students cannot identify when they play against an instructor, as opposed to a peer, they must do so by playing to sabotage all their peers' scores.
+When multiple students try to sabotage instructor scores, they also sabotage each other, and all student scores will be correspondingly lower.
+In this situation, the damage to the grader strategies' scores is representative of lower potential performance by any student strategy.
+Thus, the modified replacement-comparison scheme is sufficient.
+
+\subsection*{Auto-Grader Implementation}
+The goal of this project is not just to build a handout and an auto-grader, but to build a framework in which the development of the grader as described above requires no modification of assignment-specific code.
 Consider the components of the simulation handout:
 \begin{itemize}
-\item \texttt{runTrial} method which takes a list of strategies and simulates their behaviors in e.g.\ a college admissions simulation
-\item data processing methods, e.g.\ \texttt{oneEachTrial} which builds a list containing each configuration-specified strategy once\footnote{see figure above} and \texttt{oneEachTrials} (not shown above) which runs \texttt{oneEachTrial} a large number of times and averages the results
-\item postprocessing methods, e.g.\ to output a CSV file containing student names and their average performance in the simulation
+\item \texttt{runTrial} method which takes a list of strategies and simulates their behaviors, e.g.\ in a college admissions simulation
+\item data processing methods, e.g.\ \texttt{oneEachTrial}, which builds a list containing each configuration-specified strategy once,\footnote{see figure above} and \texttt{oneEachTrials} (not shown above), which runs \texttt{oneEachTrial} a large number of times and averages the results
+\item post-processing methods, e.g.\ outputting a CSV file containing student names and their average performance in the simulation
 \end{itemize}
@@
 \begin{itemize}
-\item two new data processing methods, \texttt{withExtraTrial} which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter\footnote{see figure above}, and a corresponding method \texttt{withExtraTrials} which averages the above.
-These are very similar to the existing data processing methods.
-\item A new postprocessing method that computes grades for each student given how many instructor strategies each student strategy beat and a lookup table.\footnote{make into figure/appendix}
+\item two new data processing methods: \texttt{withExtraTrial}, which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter\footnote{see figure above}, and a corresponding method \texttt{withExtraTrials}, which averages the above.
+These are very similar to the existing data processing methods
+\item A new post-processing method that computes grades for each student given how many instructor strategies each student strategy outperformed and a lookup table to translate this win-count to an assignment grade.
+This method, \texttt{writeGrades}, is included as appendix \footnote{TODO: make into figure/appendix}
 \end{itemize}
-\begin{verbatim}
+\begin{minted}{java}
     public static void writeGrades () {
@@
     }
-\end{verbatim}
-Given only these two changes, the handout code has been transformed into an autograder.
-Additionally, neither of these changes required alteration of the \texttt{runTrial} method, so minimal additional work (only filling in the instructor strategy names and scoring rubric) is necessary for grading an assignment once the handout has been made.
+\end{minted}
+Given only these two changes, the handout code has been transformed into an auto-grader.
+Additionally, neither of these changes required alteration of the \texttt{runTrial} method, so minimal additional work is necessary for grading an assignment once the handout has been made.
+Only filling in the instructor strategy names and scoring rubric is needed.
 
-In summary, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that postprocess the results of those trials to provide low-latency feedback or for autograding, and hooking all of the above together a \texttt{Makefile} to configure, compile, and run the assignment simulation.
+In summary, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.
 \footnote{TODO redraw using Powerpoint}
 \footnote{TODO add formatBase.py config csv}
-
+\footnote{TODO use this diagram when I talk about modularization earlier}
 \begin{figure}[hbt]
@@
 \includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
-\caption{This is a gray image.}\label{fig:gray}
+\caption{TODO: This is a gray image.}\label{fig:gray}
 \end{figure}
 
-In addition to easily altering an assignment handout into an autograder, my framework also makes it easy to build new assignments.
+In addition to easily altering an assignment handout into an auto-grader, my framework also makes it easy to build new assignments.
 To adapt the college admissions exercise described above into the elections simulation of the second problem set of COS 445 this spring, only a few changes were necessary.
-The written assignment specification describes a new interface, so a whole new interface file was necessary.
+
+Specifically, I had to develop changes only to assignment components which were not modified between the handout and the grader.
+The written assignment specification describes a new strategy format, so a new Java interface file was necessary.
 Of course, all the implementations of this interface were also written from scratch for the new assignment, all of which are fairly concise but express assignment-specific strategies.
-And finally, the \texttt{runTrial} method of the simulator had to be rewritten to simulate an election instead of college admissions, and some file names had to be changed.
-No semantic changes were necessary to the data processing or postprocessing methods for either the handout or application.
+Finally, the \texttt{runTrial} method of the simulator had to be rewritten to simulate an election instead of college admissions.
+No semantic changes were necessary to the data processing or post-processing methods for either the handout or application.
 
+\subsection*{Development of Further Tooling}
 As currently implemented, each assignment was distributed as a standalone zip file through the course website.
-Thus, even though significant code was shared between the two assignments described above, they were distributed as separate files.
-While further modularization would allow assignment-specific code describing how to simulate a game round to be separated out from code which changes within, but not between, assignments, I determined during assignment development that maintaining separate codebases for each assignment has significant advantages.
-Some simulation parameters, such as the budget constraint or number of auctioned items in an auction, the variance of student preferences in an admissions simulation, or the number of polling rounds in an election, vary between assignments.
+Even though significant code was shared between the two assignments described above, they were distributed as separate files.
+While further modularization would allow code that changes each assignment --- describing how to simulate a game round --- to be separated out from code which changes between the handout and the auto-grader, I determined during assignment development that maintaining separate code bases for each assignment has significant advantages.
+Some simulation parameters, such as the budget constraint or number of auctioned items in an auction, vary between assignments.
 Often, strategies are evaluated based on their performance relative to baseline instructor strategies in several different regimes of simulation parameters.
 This will involve tweaks to the grader code outside of the scope described above.
-While these changes are minimal and necessary, keeping details of grading separate between assignments proved useful in the real world.
+While these changes are minimal and necessary, keeping details of grading separate between assignments proves useful in the real world.
 
 Thus far, I have illustrated the strengths of my project at performing tasks which were envisioned from the outset.
-The strength of modular implementation comes also from the ability to adapt to changing demands easily in real time.
+The strength of modular implementation also comes from the ability to adapt to changing demands easily in real time.
 In this way, I was able to extend my framework throughout the semester in order to address my needs as a course assistant to remedy issues with the strategy design exercises.
 As shown below,\footnote{results section ref here} the handout code enabled students to verify that their code compiled and ran.
-However, several students submitted non-functioning strategies due to environmental differences, demonstrating the classic issue, ``Works On My Machine''.
+However, several students submitted non-functioning strategies due to environmental differences, demonstrating the classic issue ``Works On My Machine''.
 
 Other computer science courses at Princeton employ an online tool in the CS DropBox called ``Check Submit''.
-This tool allows instructors to specify tests to be run on department-configured machines using student code, and students to evaluate the performance of their submission against these tests without the concern that the software environment on their machine might not be compatible.
+This tool allows instructors to specify tests to be run on department-configured machines using student code, and enables students to evaluate the performance of their submission against these tests without the concern that the software environment on their machine might not be compatible.
 I enabled ``Check Submit'' for COS 445 strategy design exercises as a part of this work by developing simple Bash script and Makefile which adapts my assignment framework to this new setting.
-All the script has to do is copy in the assignment handout from a predefined location into the student submission folder, detect the student submission name, and write the \texttt{formatBase.py} configuration file to run their submission.
-Now, without any modification of the assignment code, every strategy design exercise automatically has DropBox ``Check Submit'' functionality possible!
+My ``Check Submit'' script copies in the assignment handout from a predefined location into the student submission folder, detect the student submission name, and write the \texttt{formatBase.py} configuration file to run their submission.
+Now, without any modification of the assignment code, every strategy design exercise automatically has DropBox ``Check Submit'' functionality possible.
 
@@
 Thus, I developed a leaderboard so students could better understand how a strategy would perform against more realistic collection of peer strategies.
-First, I initialized a new DropBox assignment for students to submit strategies to the leaderboard, which need not be their final assignment submission.
+First, I initialized a new DropBox assignment for students to submit strategies to the leaderboard, though these strategies need not be their final assignment submission.
 I implemented the leaderboard by writing a simple Bash script which scrapes all student submissions from the DropBox, automatically writes the configuration file to run every students' submission together, and runs the simulation provided in the student handout as above.
 Because the simulation output is an easy-to-parse table, I can automatically reformat it into an HTML table and place this in a web page accessible through the department web servers.
-The script to update the leaderboard runs through a cronjob at a customizable interval.
+The script to update the leaderboard runs through a \texttt{cron} job at a customizable interval.
 
@@
 I worked around this issue by disabling assertions, which were used in \texttt{runTrial} to automatically halt simulation whenever a student submission performed behavior in violation of the assignment specification.
-Then, the code automatically fell back to silently overriding illegal values from student strategies with sane but selfless defaults, and the leaderboard is correctly generated even when some student submissions are faulty.
+With this modification, the code automatically falls back to silently overriding illegal values from student strategies with sane but selfless defaults so that the leaderboard is correctly generated even when some student submissions are faulty.
 Some student code also caused compilation failures, which are more difficult to work around.
-We enabled the check submit button to leaderboard so that students could check their leaderboard strategies would compile in the department environment, and this mostly resolved the issue.
-
-The full implementation available at the course GitHub site.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s18 requires invite}
+We enabled the ``Check Submit'' button to leaderboard so that students could check their leaderboard strategies would compile in the department environment.
+This mostly resolved the issue.
 
 \section*{Results}
+This project has already achieved minimum viable product by providing a framework for implementation of strategy design exercises in the current year of COS 445.
+These assignments and the framework I developed are documented and available at the course GitHub site.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s18 requires invite}
+Thus, they will be available for reuse in future offerings of the course.
+
 As the goals of a project naturally define evaluation criteria, I have evaluated my project on the basis of each those goals: decreasing the work to build each assignment within a semester and the instructor time allocated to assignment implementation, eliminate the inter-year assignment reconstruction, improve available student resources, and in doing so improve student and instructor satisfaction.
@@
 
-%Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitiative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
+%Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
 
@@
 
-would like to not use separate files even if lots of the code is the same - complicates handout but simplifies code reuse and iteration
+would like to not use separate files even if lots of the code is the same --- complicates handout but simplifies code reuse and iteration
 
@@
 \section*{Acknowledgements}
-* matt for assignment design lead
-* course staff, especially Andreea, Ariel, Evan, Heesu, Leila, Divya, Matheus, Wei, Dylan, for grading student writeups, providing me feedback and passing along student feedback
-* david walker for iw sem (helping me stay organized and on track, helping me identify my topic)
-* iw sem peers Greg, Alex, Mel, Noah for feedback
-* jeremie for creating github repo
-* kate for providing writing help and moral support
+First of all, I would like to thank Professor Weinberg for his leadership in designing the written specifications and grading rubrics for the strategy design exercises, and for his dedication to teaching and organizing COS 445.
+His dedication to the course engaged me as a student last year and was invaluable to my work this year.
+I would like to thank Cyril Zhang for his work developing the implementation of the strategy design exercises I completed as a student, which inspired and served as a basis for this work.
+Thanks to J\'er\'emie Lumbroso for providing me with the University-owned GitHub workspace in which my project has been stored in order to preserve it for future semesters of COS 445.
+
+By grading student write-ups for strategy design exercises, Leila Clark, Wei Hu, Heesu Hwang, Dylan Mavrides, Andreea M\u{a}g\u{a}lie, Divyarthi Mohan, Ariel Schvartzman, Matheus Venturyne, and Evan Wildenhain provided me feedback about the quality of the handouts produced from my work and passed along student feedback.
+These details provided crucial insights as to the clarity of the resources I have developed and allowed me to provide targeted documentation where my code was unclear.
+Thanks also to all those students of COS 445 Spring 2018 for their feedback on the assignments used in the course, which informed my development of this project.
+
+I created this work within the framework of Professor Dave Walker's Independent Work Seminar, IW 09: ``You Be The Prof''.
+Professor Walker kept me organized and on schedule, and his guidance helped me identify and describe the topic of this work.
+I also appreciate the feedback I received throughout the semester from my peers in Professor Walker's seminar, Noah Beattie-Moss, Mel Shu, Greg Umali, and Alex Xu.
+
+I would like to thank Leila Clark and Kate Frain for their assistance revising this paper, and for their patience with my creative comma usage.
+Kate also rescued me in my darkest hours with the delivery of hot chocolate.
 
 \section*{Ethics}
-* assignments used in the course were used by the executive decision of Professor Weinberg,
-* potential conflicts of interest
-* honor code
+Where there was potential for overlap between my role as an undergraduate course assistant for COS 445 and my development of this project, I have ensured that no hours were billed for work which I have described as a part of my independent work above.
+Thus, I am not being awarded both payment as a course assistant and credit as an enrolled student for the same actions.
+Though students completed assignments developed from and optionally provided feedback for these assignments while enrolled in COS 445, these interactions were overseen and approved by Professor Weinberg.
+This paper represents my own work in accordance with university regulations.
 

### 2018-05-07 paper.tex
Conclusions and Future Work

@@
   \item empirical results about student error rates
+    ``Illegal submissions'' constitute student strategies which do not compile, throw exceptions, violate assertions, or otherwise behave outside of the parameters of the simulation.\footnote{Poorly performing strategies which obey the specification are legal.}
+    The illegal submission rate measures the percentage of students who were unable to develop a quality strategy for reasons other than lack of mastery of the course content.
   \end{itemize}
@@
 
-\section*{Conclusions}
-Through this work, I aim to improve the quality of computer science theory education, from the perspectives of both the students and faculty associated with COS 445.
+\section*{Conclusions and Future Work}
+Through this work, my goal has been to improve the quality of present and future computer science theory education, from the perspectives of both the students and faculty associated with COS 445.
 
-prisoner's dilemma + search auctions
+Student and instructor feedback indicates that my work has supported high quality strategy design exercises in the current, Spring 2018, offering of COS 445.
+Ease of development and grading of the later assignments in the course confirms that I made substantial progress in simplifying and automating the instructor experience.
+Low rates of illegal student submissions confirm that my work has allowed students to focus on core assignment content without experiencing undue difficulties with assignment structure or available tooling.
+I have achieved my goals in the present time-frame.
 
-%The goal of this project is to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition of the same work.
+I intend to continue to use these tools as a returning undergraduate course assistant when this course is taught in Spring 2019.
+However, I will graduate at the end of that semester and will be unavailable in subsequent offerings of COS 445.
+I cannot yet measure my success at preventing this work from being repeated in any future year, but Professor Weinberg has confirmed that these resources will be provided to future course staff tasked with operating the strategy design exercises.
 
@@
 
-\section*{Future Work}
+In Spring 2019, while reusing these resources, I will further simplification and automation is supported within the existing framework as I am able.
+While currently assignments are distributed independently, so no code may be shared between assignments, I will revise the assignments to share one implementation of the handout post-processor and auto-grader post-processor.
+This will complicate the assignment handout process slightly, but will simplify code reuse and iteration.
+Earlier assignments were built off of earlier versions of the infrastructure and will need to be modified where they differ from newer versions when they are reused, and sharing code between assignments will prevent this inconsistency from developing again.
 
-Some of the implementations of my infrastructure could be simplified using ClassLoaders, which would replace some of the Python code.
-This improvement was inspired by the implementation of ClassLoaders in the Spring 2014 student handout code.
+Recently, I became aware of a Java interface for loading classes at runtime.
+This technology, called ClassLoader,\footnote{https://docs.oracle.com/javase/9/docs/api/java/lang/ClassLoader.html} was implemented in the Spring 2014 handout code.
+I was unable to use ClassLoaders initially because I did not gain access to the Spring 2014 code until later in the semester.
+This simple modification will eliminate Python dependency currently required by \texttt{formatBase.py} and allow students to better understand and modify handout simulation code.
 
-would like to not use separate files even if lots of the code is the same --- complicates handout but simplifies code reuse and iteration
-
-Earlier assignments were built off of earlier versions of the infrastructure and will need to be ported to newer versions when they are reused: do next year
-
-will be reused in two years without my oversight
-
-other universities? matt through academic connections
+Though few other universities currently teach courses in algorithmic game theory as undergraduate computer science, the field is growing and such courses will inevitably become more common.
+As they do, they will look to COS 445 for resources, along with Stanford CS 269I, C.M.U.\ 15--196, and Harvard CS 136.
+It is my hope that my code could be understood and assigned such courses, with modification to suit the topics covered.
 

### 2018-05-07 paper.tex
Factor out problem background

@@
 Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
-In order to eliminate unnecessary annual replication of previous coursework development, improve course performance at scale, and improve the course experience for students, I developed an extensible framework to improve these strategy design exercises.
 
+The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
+This was accomplished by designing a modular, extensible, and reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
+Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
+
+Through this work, I aim to improve the quality of computer science theory education from the perspectives of both the students and faculty associated with COS 445.
+Quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
+
+\section*{Problem Background}
 Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
@@
 
-%TODO: move the above into the body / approach and the above as the introduction
-The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
-This was accomplished by designing a reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
-Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
-
-Through this work, I aim to improve the quality of computer science theory education from the perspectives of both the students and faculty associated with COS 445.
-Quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
+% the "programming assignments" aren't really about your ability to code.
+They are about placing the theoretical results from the course in context.
+They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.
 
@@
 
-%the "programming assignments" aren't really about your ability to code.
-They are about placing the theoretical results from the course in context.
-They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.
-
 In Spring 2019, while reusing these resources, I will further simplification and automation is supported within the existing framework as I am able.

### 2018-05-07 paper.tex
Add Matt's comments
Revise based on feedback from Kate round 2

@@
   These strategy design exercises require considerably more software infrastructure than a usual theoretical problem set would, including handout code for student self-evaluation and software auto-graders.
-  While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly structured assignments and evaluating student submissions in the context of each other.
+  While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly-structured assignments and evaluating student submissions in the context of each other.
   In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary components of these strategy design assignments.
   Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
-  This provides feedback from real student and instructor users which was used to improve the design.
+  This provides feedback from real student and instructor users, which was then used to improve the auto-grader design.
   Empirical results demonstrate the importance of quality tooling to effective use of instructor time, low broken submission rates, and high student satisfaction.
@@
 \section*{Introduction}
-My work builds upon existing programming-based game theory exercises assigned in an existing Princeton course, COS 445 ``Economics and Computing''.
-The intention of these strategy design exercises is to teach students how to use game theory to analyze a real world situation and work rationally within a healthy incentive structure where students do not try to hurt each others’ performance.
+My work builds upon existing programming-based game theory exercises assigned in Princeton's COS 445 ``Economics and Computing''.
+The intention of these strategy design exercises is to teach students how to use game theory to analyze a real-world situation and work rationally within a healthy incentive structure, e.g.\ one in which students do not try to hurt each others’ performance.
 Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
@@
 The goals of this project are to discover to what degree the development of new strategy design exercises can be simplified or automated, to improve the student resources available during the completion of these exercises, and to create institutional memory and decrease year-to-year repetition.
-This was accomplished by designing a modular, extensible, and reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, and to develop advanced automated grading tools than previously existed for the course.
+This was accomplished by designing a modular, extensible, and reusable framework which embodies the commonality between strategy design exercises, allowing instructors to create new exercises while changing only the necessary, assignment-specific details, by developing more advanced automated grading tools than previously existed for the course.
 Within this framework, I have built a collection of utilities to facilitate students' evaluation of their own strategies and to decrease strategy iteration overhead.
@@
 Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
-A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java interface}, in which two players must collaborate to receive the best outcome, but are each incentivized to defect, which results in a less preferred outcome, and have access to the other player's previous decisions when making their own decision.
+A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java interface}, in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
+Players balance the incentive to defect, which improves their own situation while damaging their opponent, with the knowledge that their opponent may defect in future rounds punish them if they defect now.
 While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
@@
 
-Students then craft strategies to play the specified game, based on their own analyses of the game's equilibrium and on which strategies they expect their peers to play.
+Students then craft strategies to play the specified game, based on their own analyses of the game's equilibrium and on which strategies they expect their peers to submit.
 These strategies are evaluated on both on their design quality and on their empirical performance.
@@
 For the search advertisement game, all the student strategies are concurrently asked to bid on the same search terms.
-They are scored based on their revenue from ad clicks less their expenditures on advertising, and each bidder knows the click-through rate for a term prior to bidding on that term.
+They are scored based on their revenue from ad clicks minus their expenditures on advertising, and each bidder knows the click-through rate for a term prior to bidding on that term.
 To create a more realistic simulation, students are graded solely on the performance of their own strategy, not on a curve of the performance of their peers.
-That is, student grades on these strategy design exercises are not zero-sum.
+That is to say, student grades on these strategy design exercises are not zero-sum.
 
@@
 This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
-In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different classical games: Prisoner's Dilemma, Centipede, and Ultimatum.
+In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different abstract games: Prisoner's Dilemma, Centipede, and Ultimatum.
 In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid.
@@
 Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
-In both semesters, Yonatan Naamad\footnote{https://github.com/ynaamad/} was responsible for software development.
+In both semesters, Yonatan Naamad,\footnote{https://github.com/ynaamad/} a former graduate student TA for the course, was responsible for software development.
 
@@
 The testing code was not designed to be automated for grading and was not modular.
-It tested manually-entered strategies against each other, and assignment-specific details, such as game structure and payoffs, were integrated within the simulation code.
+It tested manually-entered strategies against each other, and assignment-specific details such as game structure and payoffs were integrated within the simulation code.
 As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
@@
 Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
-However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke,\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly structured assignments.
+However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke,\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly-structured assignments.
 
@@
 This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
-However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and that the implementation is in Python.
+However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and the implementation is in Python.
 While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
@@
 Such systems are not applicable to this project since the strategy design exercises involve evaluation of student strategy performance in a common environment.
-Though existing automatic grading systems cannot replicate the full extend of this work, I integrate existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
-I integrated CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
+Though existing automatic grading systems cannot replicate the full extent of this work, I have integrated existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
+I integrated CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
 Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.
@@
 
-Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
-The game simulates college admissions using stable matchings.
-While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.\footnote{Kernighan and Pike chapter 4}
-I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.
-When it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trials changed from college admissions to elections.
-Additionally, when it came time to grade the problem set, I was able to modify only the post-processing step to compute grades.
-Thus, creating a new assignment required constant work in the number of framework extensions, and creating a new framework extension requires constant work in the number of assignments.
-% TODO: maybe put stuff from earlier here?
-The result of this process duplicates significant functionality from last year's assignments.
-However, because of conscious design decisions to factor out repeated code from assignment implementations, it accomplishes what previous implementations had not.
-It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
-Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
-It will be reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
-
-In order to increase the reusability, I elected to store it in a University-owned private GitHub repository and documented the repository structure and contents.
-This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.
-
-\section*{Implementation}
-% TODO: signposting
+% TODO: make it fit
 The first key decision in the implementation of these programming assignments was language selection.
-Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results}, and this would be preferred by the course staff as well.
+Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results} and this would be preferred by the course staff as well.
 Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
 Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parameterized on user-input strategy names.
-Unfortunately, COS 445 only prerequisites Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
+Unfortunately, COS 445's prerequisite courses only provide Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
 Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{COS 333 survey data}
-
 Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
@@
 Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
-However, I have not included NotNull annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
+However, I have not included \texttt{NotNull} annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
 In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}
+
+In order to increase the reusability, I elected to store this work in a University-owned private GitHub repository and documented the repository structure and contents.
+This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.
+
+\section*{Implementation}
+% TODO: signposting
+\subsection*{Preliminary Choices}
+% TODO: make it fit
+Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
+The game simulates college admissions using stable matchings.
+While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.\footnote{Kernighan and Pike chapter 4}
+I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.
+
+When it came time to implement the second strategy design exercise, I was able to reuse code which processed results of trials, even though the nature of the trials changed from college admissions to elections.
+Additionally, when it came time to grade the problem set, I was able to modify only the post-processing step to compute grades.
+Thus, creating a new assignment required constant work in the number of framework extensions, while creating a new framework extension requires constant work in the number of assignments.
+The result of this process duplicates significant functionality from last year's assignments.
+
+However, because of conscious design decisions to factor out repeated code from assignment implementations, it accomplishes what previous implementations had not.
+It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
+Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
+It will be reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
 
@@
 This is the only assignment for which I had access to both the student handout and the grader code.
-After the game design is complete, the first piece of the assignment to be implemented is the student interface:\footnote{TODO:\ make this code a figure}
+In any strategy design exercise, after the game design is complete, the next step is to implement is the student interface.
+The interface for the auctions exercise is quite simple:\footnote{TODO:\ make this code a figure}
 \begin{minted}{java}
@@
 \end{minted}
-This interface describes the necessary functions of a student strategy.
-Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results''), and they assign different values to words auctioned on different days.
-The strategy also has access the winning bids for each of the ten sponsored results from each past day and which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
+This interface describes the necessary functions of a student strategy for the auctions execise.
+Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results'') and assign different values to words auctioned on different days.
+The strategy also has access the winning bids for each of the ten sponsored results from each past day and knows which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
 This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
@@
 The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
-Zhang also implemented a program used to grade the student-submitted strategies, which consisted of two methods: \texttt{main} and \texttt{trial}.
+Zhang also implemented a program used to grade the student-submitted strategies which consisted of two methods: \texttt{main} and \texttt{trial}.
 The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
@@
 In every assignment, the tournament simulation portion (instructor-written code) is broken up into game rounds, result processing and amortization, and further post-processing, such as grade assignment and output formatting.
-The divide between game rounds and code which processes game results was present in Zhang's auction code, as the separation between the \texttt{trial} and \texttt{main} methods.
+The divide between game rounds and code which processes game results was present in Zhang's auction code as the separation between the \texttt{trial} and \texttt{main} methods.
 However, this prior work did minimal amortization and no advanced output formatting, and had no separation between them.
@@
 In the context of developing a handout to allow students to test multiple strategies of their own design, I determined that requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
-Additionally, graders desire functionality to configure the list of evaluated strategies without having to manually list out all the student strategy names and to modify this list repeatedly to identify and diagnose misbehaving student strategies.
+Additionally, graders desire functionality to configure the list of evaluated strategies without having to manually list out all the student strategy names and modify it to identify and diagnose misbehaving student strategies.
 Since Java is not able to type-check user-input strategy names, I determined that the most effective workaround for this issue would be to automatically rewrite the Java code before compile-time.
@@
 
-Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thus rewritten to instantiate one implementation of each Student class listed in the configuration file:
+Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thereby rewritten to instantiate one implementation of each Student class listed in the configuration file:
 \footnote{use figure}
@@
 While working on the assignment, students can reconfigure the testing code easily by modifying the configuration file to contain whatever strategies they want to simulate.
-For instance, given strategies \texttt{Student\_random.java} and \texttt{Student\_favorites.java} which apply to random schools and their favorite schools in the above college admissions simulation, all the student would need to do to simulate 10 submissions using the former strategy and 15 using the latter would be set the configuration file to ten lines of \texttt{random} and 15 lines of \texttt{favorites}, and then run \texttt{make test}.
-Whereas, last year, each student would have had to manually write simulation code to run the exact collection of strategies they wanted to simulate, the new handout will automatically rewrite the simulation code to simulate those strategies using \texttt{formatBase.py} and then compile and run the simulation with no additional overhead.
+For instance, given strategies \texttt{Student\_random.java} and \texttt{Student\_favorites.java}, which apply to random schools and favorite schools in the above college admissions simulation, all the student would need to do to simulate 10 submissions using the former strategy and 15 using the latter would be set the configuration file to ten lines of \texttt{random} and 15 lines of \texttt{favorites}, and then run \texttt{make test}.
+Whereas last year each student would have had to manually write simulation code to run the exact collection of strategies they wanted to simulate, the new handout will automatically rewrite the simulation code to simulate those strategies using \texttt{formatBase.py} and then compile and run the simulation with no additional overhead.
 
@@
 It is based on the following intuition: to grade a given student's strategies in a room with their peers, substitute each instructor in their place while making no other changes to the room, and measure whether the student does better or worse than that instructor would have in their place.
-The performance of a student strategy $S_i$ among strategies $S_1 \ldots S_n$, pro-rated based on the potential best and worst possible performances by any strategy in the simulation, can be captured by comparing the score $x_i$ of $S_i$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$ to the scores $y_{i,1} \ldots y_{i,m}$ of a predetermined menagerie of $m$ instructor strategies $I_1 \ldots I_m$, where each $y_{i,j}$ in $y_{i,1} \ldots y_{i,m}$ is the score of $I_j$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$.
+The performance of a student strategy $S_i$ among strategies $S_1 \ldots S_n$, pro-rated based on the potential best and worst possible performances by any strategy in the simulation can be captured by comparing the score $x_i$ of $S_i$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$ to the scores $y_{i,1} \ldots y_{i,m}$ of a predetermined menagerie of $m$ instructor strategies $I_1 \ldots I_m$, where each $y_{i,j}$ in $y_{i,1} \ldots y_{i,m}$ is the score of $I_j$ against $S_1 \ldots S_{i-1}, S_{i+1} \ldots S_n$.
 Students whose strategies outperform all instructor-designed strategies have done better than the instructors would have at the assignment, and receive the best grades.
@@
 
-This grading strategy has the correct incentives: each student will only work to maximize their chance of beating each instructor threshold, and not to sabotage their peers' performance.
+This grading strategy has the correct incentives: each student will work to maximize their chance of beating each instructor threshold, not to sabotage their peers' performance.
 Since the instructor strategies used for grading are not revealed and the pool of other student submissions is unpredictable, the distribution of instructor thresholds approaches uniform, and students will attempt to beat as much of the real interval of the score range as possible, producing the same behavior as students maximizing expectation.
@@
 Thus, students are not incentivized to play a lower-expectation strategy in order to increase their variance.\footnote{The same analysis holds for all higher moments of their strategy.}
-This system is not vulnerable to students attempting to sabotage instructor scores for their own benefit, since instructor scores for a given student are calculated without the play of this student.
+This system is also not vulnerable to students attempting to sabotage instructor scores for their own benefit, since instructor scores for a given student are calculated without the play of this student.
 
@@
 $, this is a performance improvement; for practical reasons, all simulations used in this course take polynomial time in the number of students.}
-The modified replacement-comparison grading scheme measures student scores $x_1 \ldots x_n$ for all students $S_1 \ldots S_n$ amortized across many trials, then for each instructor strategies $I_j$ among $I_1 \ldots I_m$, measures their score $y_j$ against all of $S_1 \ldots S_n$.
-That is to say, instructor strategies are assigned scores based on their performance against all the students, while student strategies are assigned scores based on their performance against all the other students.
+The modified replacement-comparison grading scheme measures student scores $x_1 \ldots x_n$ for all students $S_1 \ldots S_n$ amortized across many trials, and then measures $y_j$ against all of $S_1 \ldots S_n$ for each instructor strategy $I_j$ among $I_1 \ldots I_m$.
+That is to say, instructor strategies are assigned $y_j$ based on their performance against all the students, while student strategies are assigned $x_i$ based on their performance against all the other students.
+Student grades are still assigned based on how many instructor strategies performed worse than their strategy, computed as $\sum\limits_{i=1}^n \delta_{x_i > y_j}$ as before.
 
@@
 Now, without any modification of the assignment code, every strategy design exercise automatically has DropBox ``Check Submit'' functionality possible.
+This confirms to students that their strategy will not be incompatible with the grading environment, improving student satisfaction with the course.
 
-This confirms to students that their strategy will not be incompatible with the grading environment, improving student satisfaction with the course.
 However, students would still benefit from more realistic testing.
@@
 
+%What are your thoughts on how well the strategy design exercises have gone this year?
+Specifically, I'm interested in your satisfaction with the implementations and software, and the amount of instructor time and frustration spent.
+(And less intersted in comments on the course policy decisions that may have impacted how well they went, sicne that's not in the scope of my independent work.)
+%** significantly** improved instructor involvement.
+
+%I didn't actually touch any of the software directly, so I don't know how to comment on that.
+But I felt like the challenges mostly ran themselves.
+We talked briefly to set it up.
+We talked briefly to decide how to grade, and I didn't have to answer any technical questions for students in between
+
 \section*{Conclusions and Future Work}
@@
 
-Student and instructor feedback indicates that my work has supported high quality strategy design exercises in the current, Spring 2018, offering of COS 445.
+Student and instructor feedback indicates that my work has supported high quality strategy design exercises in the current Spring 2018 offering of COS 445.
 Ease of development and grading of the later assignments in the course confirms that I made substantial progress in simplifying and automating the instructor experience.
@@
 
-In Spring 2019, while reusing these resources, I will further simplification and automation is supported within the existing framework as I am able.
-While currently assignments are distributed independently, so no code may be shared between assignments, I will revise the assignments to share one implementation of the handout post-processor and auto-grader post-processor.
+In Spring 2019, as supported within my existing framework, I will further simplify and automate the assignments.
+While currently assignments are distributed independently, so no code may be shared between assignments, I will revise assignments to share one implementation of the handout post-processor and auto-grader post-processor.
 This will complicate the assignment handout process slightly, but will simplify code reuse and iteration.
-Earlier assignments were built off of earlier versions of the infrastructure and will need to be modified where they differ from newer versions when they are reused, and sharing code between assignments will prevent this inconsistency from developing again.
+Earlier assignments were built off of earlier versions of the infrastructure and will need to be modified where they differ from newer versions when they are reused, but sharing code between assignments will prevent this inconsistency from developing again.
 

### 2018-05-07 paper.tex
Much revision and starting results

@@
 \title{
-A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises}
+  A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises
+}
 
@@
 
-While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand considerable instructor resources be dedicated to building and grading software resources, which have historically been significantly rebuilt for each assignment.
+These strategy design exercises are intended to help students place theoretical results from the course in context.
+They create a scenario in which mastery of theoretical course content is demonstrated by making and justifying real-world decisions.
+Professor Weinberg's intent is that no student should experience difficulty implementing their strategy, and all of the challenge should come from developing a creative, successful strategy.
+
+While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
 Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
 Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
-
-% the "programming assignments" aren't really about your ability to code.
-They are about placing the theoretical results from the course in context.
-They create a scenario in which mastery of theoretical results from the course content is demonstrated by making and justifying real-world decisions.
 
@@
 This software would naturally grow throughout development as demanded by the needs of the course, and the final product will naturally lower-bound the maximum degree of automation and modularity possible.
+While this decision to develop my software using agile methods obviates the need for an extensive design process, a few key decisions were still needed before implementation could commence.
 
-% TODO: make it fit
-The first key decision in the implementation of these programming assignments was language selection.
+While I was initially inclined to pursue implementation in Java, I spent considerable effort on language selection to verify this decision.
+This was necessary because I would incur a considerable cost to myself and to others ere I to change programming languages partway through the semester.
+I would have to rebuild all previous work, and I would inconvenience all the students of COS 445 by making them change languages and wasting their time learning the abandoned language.
+
 Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results} and this would be preferred by the course staff as well.
@@
 
-In order to increase the reusability, I elected to store this work in a University-owned private GitHub repository and documented the repository structure and contents.
+While of lesser urgency, I have also planned ahead to ensure the reusability of my work.
+I elected to store this work in a University-owned private GitHub repository.
+I also documented the repository structure and contents, including a summary of the process of developing and deploying a new assignment.
 This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.
@@
 % TODO: signposting
-\subsection*{Preliminary Choices}
 % TODO: make it fit
@@
 
-However, because of conscious design decisions to factor out repeated code from assignment implementations, it accomplishes what previous implementations had not.
-It will be modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
-Throughout the semester, I can leverage my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
-It will be reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
+However, because of conscious design decisions to factor out repeated code from assignment implementations, my implementation has accomplished what previous implementations had not.
+It is modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
+Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
+It is reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
+\footnote{TODO redraw using Powerpoint}
+\footnote{TODO use this diagram when I talk about modularization earlier}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
+  \caption{TODO: This is a gray image.}\label{fig:gray}
+\end{figure}
 
@@
 However, in order to design the auto-grader, Professor Weinberg and I had to develop a well-specified, portable standard for grading strategy design exercises.
-A key constraint in the grading of these assignments is that the incentive for the students must be to try to maximize their own strategy's performance.
+A key constraint in the grading of these assignments is that the students must be incentivized to maximize their own strategy's performance, and not incentivized to either help or hurt their peers except when doing so helps themselves.\footnote{Of course, students are encouraged to help their peers out of their own compassion, and doing so contributes to their course participation grade, but they are not rewarded for doing so in their assignment.}
 Therefore, curving each student's grade based on the percentile of their strategy's performance is not acceptable.
@@
 \begin{itemize}
-\item \texttt{runTrial} method which takes a list of strategies and simulates their behaviors, e.g.\ in a college admissions simulation
-\item data processing methods, e.g.\ \texttt{oneEachTrial}, which builds a list containing each configuration-specified strategy once,\footnote{see figure above} and \texttt{oneEachTrials} (not shown above), which runs \texttt{oneEachTrial} a large number of times and averages the results
-\item post-processing methods, e.g.\ outputting a CSV file containing student names and their average performance in the simulation
+\item
+  \texttt{runTrial} method which takes a list of strategies and simulates their behaviors, e.g.\ in a college admissions simulation
+\item
+  data processing methods, e.g.\ \texttt{oneEachTrial}, which builds a list containing each configuration-specified strategy once,\footnote{see figure above} and \texttt{oneEachTrials} (not shown above), which runs \texttt{oneEachTrial} a large number of times and averages the results
+\item
+  post-processing methods, e.g.\ outputting a CSV file containing student names and their average performance in the simulation
 \end{itemize}
@@
 \begin{itemize}
-\item two new data processing methods: \texttt{withExtraTrial}, which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter\footnote{see figure above}, and a corresponding method \texttt{withExtraTrials}, which averages the above.
+\item
+  two new data processing methods: \texttt{withExtraTrial}, which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter\footnote{see figure above}, and a corresponding method \texttt{withExtraTrials}, which averages the above.
   These are very similar to the existing data processing methods
-\item A new post-processing method that computes grades for each student given how many instructor strategies each student strategy outperformed and a lookup table to translate this win-count to an assignment grade.
+\item
+  A new post-processing method that computes grades for each student given how many instructor strategies each student strategy outperformed and a lookup table to translate this win-count to an assignment grade.
   This method, \texttt{writeGrades}, is included as appendix \footnote{TODO: make into figure/appendix}
@@
 
-In summary, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.
-\footnote{TODO redraw using Powerpoint}
+In summary, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.\footnote{add ref to above diagram here}
 \footnote{TODO add formatBase.py config csv}
-\footnote{TODO use this diagram when I talk about modularization earlier}
-\begin{figure}[hbt]
-\centering
-\includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
-\caption{TODO: This is a gray image.}\label{fig:gray}
-\end{figure}
 
@@
 In this way, I was able to extend my framework throughout the semester in order to address my needs as a course assistant to remedy issues with the strategy design exercises.
-As shown below,\footnote{results section ref here} the handout code enabled students to verify that their code compiled and ran.
-However, several students submitted non-functioning strategies due to environmental differences, demonstrating the classic issue ``Works On My Machine''.
+While the handout code enabled students to verify that their code compiled and ran on their own personal computers, several students submitted non-functioning strategies due to environmental differences, demonstrating the classic issue ``Works On My Machine''.
 
@@
 
-As the goals of a project naturally define evaluation criteria, I have evaluated my project on the basis of each those goals: decreasing the work to build each assignment within a semester and the instructor time allocated to assignment implementation, eliminate the inter-year assignment reconstruction, improve available student resources, and in doing so improve student and instructor satisfaction.
+While I have been unable to experimentally determine whether my project will be reused, I have evaluated my successful achievement of each other goal.
+I have decreased the work to build each assignment within a semester and the instructor time allocated to assignment implementation, eliminated the inter-year assignment reconstruction, and improved available student resources
+These achievements have increased student and instructor satisfaction with the strategy design exercises.
 
+My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment to assignment rewriting.
 \begin{itemize}
-\item discover modularity and decrease assignment to assignment rewriting
-  \begin{itemize}
-  \item code rewriting measurements
+\item code rewriting measurements between assignments
 \item instructor time usage
+\item extensibility:
 \end{itemize}
-\item improve student resources
+
+I have also succeeded at leveraging the extensibility of my project to improve student resources.
+
 \begin{itemize}
@@
 \end{itemize}
-\item create institutional memory and decrease year-to-year rewriting
-  \begin{itemize}
-  \item cant measure until next year, but set up for it
-  \end{itemize}
-\item increase student and instructor satisfaction
+
+Through this work, I have improved student and instructor experiences.
+In addition to the data gathered above, I verified this achievement by surveying the current students of COS 445 under the supervision of Professor Weinberg.
 \begin{itemize}
@@
 \end{itemize}
-\end{itemize}
 
-%Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
+% Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
 
-%What are your thoughts on how well the strategy design exercises have gone this year?
+% What are your thoughts on how well the strategy design exercises have gone this year?
 Specifically, I'm interested in your satisfaction with the implementations and software, and the amount of instructor time and frustration spent.
 (And less intersted in comments on the course policy decisions that may have impacted how well they went, sicne that's not in the scope of my independent work.)
-%** significantly** improved instructor involvement.
 
-%I didn't actually touch any of the software directly, so I don't know how to comment on that.
+% ** significantly** improved instructor involvement.
+% I didn't actually touch any of the software directly, so I don't know how to comment on that.
 But I felt like the challenges mostly ran themselves.

### 2018-05-07 paper.tex
Set up for citations

@@
 \newcommand{\quotes}[1]{``#1''}
+
+\usepackage{appendix}
+\usepackage{titling}
 
@@
 
-\author{Andrew Wonnacott\\
-  Advisers: Professor Dave Walker, Professor Matt Weinberg}
+\author{
+  Andrew Wonnacott\\
+  Advisers: Professor Dave Walker, Professor Matt Weinberg
+}
 
@@
 
-\thispagestyle{empty}
 \doublespacing{}
+
+\begin{titlingpage}
   \begin{abstract}
@@
   \end{abstract}
+\end{titlingpage}
 
-\newpage
 \section*{Introduction}
@@
 Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
-Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
+Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}~\cite{coursesizes}
 
@@
 For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
-The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
+The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.~\cite{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
 It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
@@
 Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
-A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java interface}, in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
+A classic iterated game is the iterated prisoner's dilemma,\footnote{Figure: PD game -> Java interface} in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
 Players balance the incentive to defect, which improves their own situation while damaging their opponent, with the knowledge that their opponent may defect in future rounds punish them if they defect now.
@@
 
-While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
+While the strategy design exercises assignments are popular with students~\cite{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
 Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
-Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.
+Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused run-time exceptions, requiring considerable additional instructor resources.
 
 \section*{Related Work}
-This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
+This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.~\cite{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
 In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different abstract games: Prisoner's Dilemma, Centipede, and Ultimatum.
-In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid.
+In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{A G.S.P.\ auction is an auction of multiple items, one after another, where the winning bid pays the second highest bid.
 This is the auction format used by Google to sell sponsored search auctions.}
 
-Both problem sets were implemented and graded by Cyril Zhang\footnote{https://github.com/cyrilzhang}, a graduate student TA for the course.
-Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
+Both problem sets were implemented and graded by Cyril Zhang~\cite{https://github.com/cyrilzhang}, a graduate student TA for the course.
+Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
 However, his implementation of software for strategy design assignments was intended for grader use only.
@@
 
-Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
+Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014~\cite{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
 Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
-In both semesters, Yonatan Naamad,\footnote{https://github.com/ynaamad/} a former graduate student TA for the course, was responsible for software development.
+In both semesters, Yonatan Naamad,~\cite{https://github.com/ynaamad/} a former graduate student TA for the course, was responsible for software development.
 
-The only resources available from Fall 2012 were collected from the course Google Code repository.\footnote{https://code.google.com/archive/p/cos445-scripts/}
+The only resources available from Fall 2012 were collected from the course Google Code repository.~\cite{https://code.google.com/archive/p/cos445-scripts/}
 This repository contains incomplete Python skeleton code for a basic tournament of an unspecified game.
-I uploaded this code to the current course repository\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.
+I uploaded this code to the current course repository~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.
 
-The Spring 2014 iteration of the course was developed on a private GitHub repository.\footnote{https://github.com/ynaamad/cos445}
+The Spring 2014 iteration of the course was developed on a private GitHub repository.~\cite{https://github.com/ynaamad/cos445}
 Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
@@
 As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
-These resources were uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.
+These resources were uploaded to the current course repository,~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.
 
 Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
-However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke,\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly-structured assignments.
+However, a survey of several universities' courses, including courses at Harvard~\cite{https://beta.blogs.harvard.edu/k108875/}, Stanford~\cite{https://theory.stanford.edu/~tim/364a.html}~\cite{https://theory.stanford.edu/~tim/f16/f16.html}, Cornell~\cite{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington~\cite{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale~\cite{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn~\cite{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech~\cite{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon~\cite{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke~\cite{https://www2.cs.duke.edu/courses/spring16/compsci590.4/}, identified only one other course with similarly-structured assignments.
 
-Harvard's Computer Science 136, ``Economics and Computation'',\footnote{https://beta.blogs.harvard.edu/k108875/assignments/} assigns two programming problem sets.
-The first requires implementation of a peer-to-peer file sharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
+Harvard's Computer Science 136, ``Economics and Computation''~\cite{https://beta.blogs.harvard.edu/k108875/assignments/}, assigns two programming problem sets.
+The first requires implementation of a peer-to-peer file sharing system similar to BitTorrent, a protocol in which incentives parallel Prisoner's Dilemma.
 However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
@@
 Though existing automatic grading systems cannot replicate the full extent of this work, I have integrated existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
-I integrated CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
+I integrated CS DropBox~\cite{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
 Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.
@@
 
-Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results} and this would be preferred by the course staff as well.
+Many students suggested the assignments be implemented in Python,~\cite{per survey 1 results} and this would be preferred by the course staff as well.
 Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
@@
 Unfortunately, COS 445's prerequisite courses only provide Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
-Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{COS 333 survey data}
+Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.~\cite{COS 333 survey data}
 Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
@@
 For instance, Java objects used as function parameters are passed by mutable, nullable reference.
-This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and nonnull unless otherwise explicitly specified.
-Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
+This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and non-null unless otherwise explicitly specified.
+Current industry standards for Java code obviate both of these issues using modern language features.~\cite{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}~\cite{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}~\cite{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
 In order to preserve backwards compatibility, these features are not implemented by default.
@@
 However, I have not included \texttt{NotNull} annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
-In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}
+In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.~\cite{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}
 
-While of lesser urgency, I have also planned ahead to ensure the reusability of my work.
+While of lesser urgency, I have also planned ahead to ensure the re-usability of my work.
 I elected to store this work in a University-owned private GitHub repository.
@@
 The game simulates college admissions using stable matchings.
-While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.\footnote{Kernighan and Pike chapter 4}
+While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.~\cite{Kernighan and Pike chapter 4}
 I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.
@@
 It is reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
-\footnote{TODO redraw using Powerpoint}
-\footnote{TODO use this diagram when I talk about modularization earlier}
+% TODO redraw using Powerpoint
+% TODO use this diagram when I talk about modularization earlier
 \begin{figure}[hbt]
@@
 \subsection*{Handout Implementation}
-In order to design my framework, I reviewed non-modularized code from the Spring 2017 auctions exercise.
+In order to design my framework, I reviewed non-modular code from the Spring 2017 auctions exercise.
 This is the only assignment for which I had access to both the student handout and the grader code.
 In any strategy design exercise, after the game design is complete, the next step is to implement is the student interface.
-The interface for the auctions exercise is quite simple:\footnote{TODO:\ make this code a figure}
+The interface for the auctions exercise is quite simple, as shown in Figure~\ref{minted:Bidder}.
+\begin{figure}[hbt]
 \begin{minted}{java}
@@
 \end{minted}
-This interface describes the necessary functions of a student strategy for the auctions execise.
+  \caption{\texttt{interface Bidder} demonstrates a strategy interface}\label{minted:Bidder}
+\end{figure}
+This interface describes the necessary functions of a student strategy for the auctions exercise.
 Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results'') and assign different values to words auctioned on different days.
@@
 During the development of this handout, however, the statically-typed nature of Java raised some difficulty.
-Zhang's grader code had student submission names hardcoded into complex expressions, as though they had been copied in from a manually-written list formatted using \texttt{sed}.
+Zhang's grader code had student submission names hard-coded into complex expressions, as though they had been copied in from a manually-written list formatted using \texttt{sed}.
 In the context of developing a handout to allow students to test multiple strategies of their own design, I determined that requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
@@
 
-For this purpose, I developed a simple Python script capable of rewriting arbitrary template plaintext files using a CSV file.
-This script, \texttt{formatBase.py},\footnote{TODO: appendix this} builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
+For this purpose, I developed a simple Python script capable of rewriting arbitrary template plain-text files using a CSV file.
+This script, \texttt{formatBase.py}, included as Appendix~\ref{appendix:formatBase}, builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
 In its input, it identifies lines which start with \texttt{//R} and end with \texttt{//}.
@@
 Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thereby rewritten to instantiate one implementation of each Student class listed in the configuration file:
-\footnote{use figure}
+\begin{figure}[hbt]
 \begin{minted}{java}
@@
 \end{minted}
+  \caption{\texttt{oneEachTrial} demonstrates usage of \texttt{formatBase.py}}\label{minted:oneEachTrial}
+\end{figure}
+
 My modular design allows for data collection code to vary without additional overhead.
@@
 This method is useful for grading assignments.
-\footnote{todo: figure}
+\begin{figure}[hbt]
 \begin{minted}{java}
@@
 \end{minted}
+  \caption{\texttt{withExtraTrial} demonstrates modularity in data processing}\label{minted:withExtraTrial}
+\end{figure}
 
@@
 While working on the assignment, students can reconfigure the testing code easily by modifying the configuration file to contain whatever strategies they want to simulate.
-For instance, given strategies \texttt{Student\_random.java} and \texttt{Student\_favorites.java}, which apply to random schools and favorite schools in the above college admissions simulation, all the student would need to do to simulate 10 submissions using the former strategy and 15 using the latter would be set the configuration file to ten lines of \texttt{random} and 15 lines of \texttt{favorites}, and then run \texttt{make test}.
+For instance, given strategies \texttt{Student\_random.java} and \texttt{Student\_favorites.java}, which apply to random schools and favorite schools in the above college admissions simulation, all the student would need to do to simulate ten submissions using the former strategy and 15 using the latter would be set the configuration file to ten lines of \texttt{random} and 15 lines of \texttt{favorites}, and then run \texttt{make test}.
+Such a configuration file is included as Appendix~\ref{appendix:students}.
 Whereas last year each student would have had to manually write simulation code to run the exact collection of strategies they wanted to simulate, the new handout will automatically rewrite the simulation code to simulate those strategies using \texttt{formatBase.py} and then compile and run the simulation with no additional overhead.
@@
 For instance, in an iterated prisoner's dilemma, if students are graded based on relative performance, then they are apathetic between both cooperating and both defecting.
-So there is no incentive under any circumstance to cooperate, even in the face of potentially irrational counterparties, and every student should always defect.
+So there is no incentive under any circumstance to cooperate, even in the face of potentially irrational counter-parties, and every student should always defect.
 
@@
 \item
-  data processing methods, e.g.\ \texttt{oneEachTrial}, which builds a list containing each configuration-specified strategy once,\footnote{see figure above} and \texttt{oneEachTrials} (not shown above), which runs \texttt{oneEachTrial} a large number of times and averages the results
+  data processing methods, e.g.\ \texttt{oneEachTrial} (Figure~\ref{minted:oneEachTrial}), which builds a list containing each configuration-specified strategy once, and \texttt{oneEachTrials} (not shown above), which runs \texttt{oneEachTrial} a large number of times and averages the results
 \item
@@
 \end{itemize}
+
 Only the first of these contains assignment-specific code.
 In order to implement replacement-comparison grading, I implemented the following methods:
+
 \begin{itemize}
 \item
-  two new data processing methods: \texttt{withExtraTrial}, which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter\footnote{see figure above}, and a corresponding method \texttt{withExtraTrials}, which averages the above.
+  two new data processing methods: \texttt{withExtraTrial} (Figure~\ref{minted:withExtraTrial}), which builds a list containing each configuration-specified strategy once, and one extra strategy passed in as a parameter, and a corresponding method \texttt{withExtraTrials}, which averages the above.
   These are very similar to the existing data processing methods
@@
   A new post-processing method that computes grades for each student given how many instructor strategies each student strategy outperformed and a lookup table to translate this win-count to an assignment grade.
-  This method, \texttt{writeGrades}, is included as appendix \footnote{TODO: make into figure/appendix}
+  This method, \texttt{writeGrades}, is included as Appendix~\ref{appendix:writeGrades}
 \end{itemize}
-\begin{minted}{java}
-    public static void writeGrades () {
-        final int numTrials = 1;
-        //R netids[{0}] = "{netID}";//
-        // defaults as specified in assignment handout PDF
-        final double S = 100, T = 100, W = 10;
-        // Compute x_i
-        double[] oneEachTrials = oneEachTrials(100, S, T, W);
 
-        // Instructor strategies
-        List<Class<? extends Student>> ourStrats =
-            new ArrayList<Class<? extends Student>>();
-        ourStrats.add(Student_REDACTED.class);
-        // a total of twelve such lines like the above line
-        double[] winsToPoints = new double[]{
-            0, 0.5, 1.0, 1.2, 1.5, 1.8, 2, 3, 3.5, 4.0, 4.5, 4.8, 5
-        };
-        // Compute \sum_j \delta_{x_i > y_j} for all i
-        int[] wins = new int[N];
-        for (Class<? extends Student> strat : ourStrats) {
-            double[] res = withExtraTrials(strat, numTrials, S, T, W);
-            for (int i = 0; i < N; ++i) {
-                if (res[i] > res[N]) {
-                    ++wins[i];
-                }
-            }
-        }
-        // Output grades as csv
-        System.out.println("netID,points");
-        for (int i = 0; i < N; ++i) {
-            System.out.println(netids[i] + "," + Double.toString(oneEachTrials[i])
-                               + "," + Double.toString(winsToPoints[wins[i]]));
-        }
-    }
-\end{minted}
 Given only these two changes, the handout code has been transformed into an auto-grader.
@@
 
-In summary, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.\footnote{add ref to above diagram here}
-\footnote{TODO add formatBase.py config csv}
+In summary, as described in Figuree~\ref{figure:outline}, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.
 
@@
 
-Other computer science courses at Princeton employ an online tool in the CS DropBox called ``Check Submit''.
+Other computer science courses at Princeton employ an online tool in the CS Dropbox called ``Check Submit''.
 This tool allows instructors to specify tests to be run on department-configured machines using student code, and enables students to evaluate the performance of their submission against these tests without the concern that the software environment on their machine might not be compatible.
@@
 My ``Check Submit'' script copies in the assignment handout from a predefined location into the student submission folder, detect the student submission name, and write the \texttt{formatBase.py} configuration file to run their submission.
-Now, without any modification of the assignment code, every strategy design exercise automatically has DropBox ``Check Submit'' functionality possible.
+Now, without any modification of the assignment code, every strategy design exercise automatically has Dropbox ``Check Submit'' functionality possible.
 This confirms to students that their strategy will not be incompatible with the grading environment, improving student satisfaction with the course.
@@
 Thus, I developed a leaderboard so students could better understand how a strategy would perform against more realistic collection of peer strategies.
-First, I initialized a new DropBox assignment for students to submit strategies to the leaderboard, though these strategies need not be their final assignment submission.
-I implemented the leaderboard by writing a simple Bash script which scrapes all student submissions from the DropBox, automatically writes the configuration file to run every students' submission together, and runs the simulation provided in the student handout as above.
+First, I initialized a new Dropbox assignment for students to submit strategies to the leaderboard, though these strategies need not be their final assignment submission.
+I implemented the leaderboard by writing a simple Bash script which scrapes all student submissions from the Dropbox, automatically writes the configuration file to run every students' submission together, and runs the simulation provided in the student handout as above.
 Because the simulation output is an easy-to-parse table, I can automatically reformat it into an HTML table and place this in a web page accessible through the department web servers.
@@
 This project has already achieved minimum viable product by providing a framework for implementation of strategy design exercises in the current year of COS 445.
-These assignments and the framework I developed are documented and available at the course GitHub site.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s18 requires invite}
+These assignments and the framework I developed are documented and available at the course GitHub site.~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s18 requires invite}
 Thus, they will be available for reuse in future offerings of the course.
@@
 
-My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment to assignment rewriting.
+My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment-to-assignment rewriting.
 \begin{itemize}
@@
 \item empirical results about student error rates
-  ``Illegal submissions'' constitute student strategies which do not compile, throw exceptions, violate assertions, or otherwise behave outside of the parameters of the simulation.\footnote{Poorly performing strategies which obey the specification are legal.}
+  ``Illegal submissions'' constitute student strategies which do not compile, throw exceptions, violate assertions, or otherwise behave outside of the parameters of the simulation.~\cite{Poorly performing strategies which obey the specification are legal.}
   The illegal submission rate measures the percentage of students who were unable to develop a quality strategy for reasons other than lack of mastery of the course content.
@@
 
-Recently, I became aware of a Java interface for loading classes at runtime.
-This technology, called ClassLoader,\footnote{https://docs.oracle.com/javase/9/docs/api/java/lang/ClassLoader.html} was implemented in the Spring 2014 handout code.
+Recently, I became aware of a Java interface for loading classes at run time.
+This technology, called ClassLoader,~\cite{https://docs.oracle.com/javase/9/docs/api/java/lang/ClassLoader.html} was implemented in the Spring 2014 handout code.
 I was unable to use ClassLoaders initially because I did not gain access to the Spring 2014 code until later in the semester.
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 First of all, I would like to thank Professor Weinberg for his leadership in designing the written specifications and grading rubrics for the strategy design exercises, and for his dedication to teaching and organizing COS 445.
@@
 
-I created this work within the framework of Professor Dave Walker's Independent Work Seminar, IW 09: ``You Be The Prof''.
+I created this work within the framework of Professor Dave Walker's Independent Work Seminar, I.W.\ 09: ``You Be The Prof''.
 Professor Walker kept me organized and on schedule, and his guidance helped me identify and describe the topic of this work.
@@
 
+\newpage
+\begin{appendices}
+  \singlespacing{}
+  \appendixpage{}
+  \section{\texttt{writeGrades} demonstrates modularity in post-processing}\label{appendix:writeGrades}
+\begin{minted}{java}
+    public static void writeGrades () {
+        final int numTrials = 1;
+        //R netids[{0}] = "{netID}";//
+        // defaults as specified in assignment handout PDF
+        final double S = 100, T = 100, W = 10;
+        // Compute x_i
+        double[] oneEachTrials = oneEachTrials(100, S, T, W);
+
+        // Instructor strategies
+        List<Class<? extends Student>> ourStrats =
+            new ArrayList<Class<? extends Student>>();
+        ourStrats.add(Student_REDACTED.class);
+        // a total of twelve such lines like the above line
+        double[] winsToPoints = new double[]{
+            0, 0.5, 1.0, 1.2, 1.5, 1.8, 2, 3, 3.5, 4.0, 4.5, 4.8, 5
+        };
+        // Compute \sum_j \delta_{x_i > y_j} for all i
+        int[] wins = new int[N];
+        for (Class<? extends Student> strat : ourStrats) {
+            double[] res = withExtraTrials(strat, numTrials, S, T, W);
+            for (int i = 0; i < N; ++i) {
+                if (res[i] > res[N]) {
+                    ++wins[i];
+                }
+            }
+        }
+        // Output grades as CSV
+        System.out.println("netID,points");
+        for (int i = 0; i < N; ++i) {
+            System.out.println(netids[i]
+                               + ","
+                               + Double.toString(oneEachTrials[i])
+                               + ","
+                               + Double.toString(winsToPoints[wins[i]]));
+        }
+    }
+\end{minted}
+  \newpage
+  \section{\texttt{formatBase.py} was used to automatically reconfigure the strategies to be simulated}\label{appendix:formatBase}
+\begin{minted}{python}
+import csv
+import sys
+
+def main():
+    """
+    Formats the standard input to standard output.
+    Replaces lines of the form [\s]*//R(.*)//[\s]* with a line for every
+    row of data.csv with the central string formatted according to the
+    row of data.csv. Replaces lines of the form [\s]*//L(.*)//[\s]* with
+    the central string formatted with the number of rows.
+    """
+    if len(sys.argv) != 2:
+        sys.exit("Usage: {} [data.csv] < [ClassBase.java] > [Class.java]"
+                 .format(sys.argv[0]))
+
+    with open(sys.argv[1]) as f:
+        reader = csv.DictReader(f, skipinitialspace=True)
+        rows = [{k: v for k, v in row.items()} for row in reader]
+
+    for line_ in sys.stdin:
+        line_ = line_.rstrip()
+        line = line_.strip()
+        if line.startswith("//L") and line.endswith("//"):
+            print(line[3:-2].format(len(rows)))
+
+        elif line.startswith("//R") and line.endswith("//"):
+            for i, vals in enumerate(rows):
+                print(line[3:-2].format(i, **vals))
+
+        else:
+            print(line_)
+
+if __name__ == "__main__":
+    main()
+
+\end{minted}
+
+  \newpage
+  \section{\texttt{students.csv} provides an example configuration for \texttt{formatBase.py}}\label{appendix:students}
+\begin{verbatim}
+netID
+random
+random
+random
+random
+random
+random
+random
+random
+random
+random
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+favorites
+\end{verbatim}
+\end{appendices}
 \end{document}
+
+%  LocalWords:  Wonnacott LocalWords writeGrades modularity Xu Zhang
+%  LocalWords:  Wildenhain baselinestretch matchings cryptocurrencies
+%  LocalWords:  cryptocurrency blockchain Zhang's Yonatan Braverman
+%  LocalWords:  CAS PHP leaderboard iteratively programatically Ocaml
+%  LocalWords:  nullable unmodifiable NotNull Kernighan Shapley myBid
+%  LocalWords:  dailyValue myPayment addResults getBid sed CSV py hbt
+%  LocalWords:  formatBase netID oneEachTrial runTrial withExtraTrial
+%  LocalWords:  clazz ReflectiveOperationException printStackTrace Hu
+%  LocalWords:  incentivized Makefile modularization cron emie Heesu
+%  LocalWords:  customizable extensibility ClassLoaders Lumbroso Shu
+%  LocalWords:  Hwang Mavrides Andreea Divyarthi Mohan Schvartzman
+%  LocalWords:  Matheus Venturyne Beattie Frain Umali numTrials strat
+%  LocalWords:  netids oneEachTrials ourStrats ArrayList winsToPoints
+%  LocalWords:  withExtraTrials toString Naamad

### 2018-05-07 paper.tex
Start biber

@@
 \newcommand{\quotes}[1]{``#1''}
+
+\usepackage[english]{babel}
+\usepackage{csquotes}
+\usepackage{biblatex}
 
@@
 \usepackage[normalem]{ulem}
+
+\addbibresource{references.bib}
 
@@
 \section*{Implementation}
-% TODO: signposting
-% TODO: make it fit
 Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
@@
 
-However, because of conscious design decisions to factor out repeated code from assignment implementations, my implementation has accomplished what previous implementations had not.
-It is modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
-Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
-It is reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
-% TODO redraw using Powerpoint
-% TODO use this diagram when I talk about modularization earlier
+However, because of conscious design decisions to factor out repeated code within each assignment, my project will be more reusable than implementations from past semesters.
+It is also extensible, so new extensions such as additional tools or interfaces can be written for strategy design exercises.
+The structure of my project is outlined in Figure~\ref{fig:outline}.
+The modular layout ensures that each component can be designated as either reusable between assignments (green), written for each assignment by the instructors (blue), or submitted by each student for each assignment (orange).
+Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce extensions, including CS Dropbox ``Check Submit'' functionality and a student strategy leaderboard.
+This framework reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
+
 \begin{figure}[hbt]
   \centering
-  \includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
-  \caption{TODO: This is a gray image.}\label{fig:gray}
+  \includegraphics[scale=0.75]{outline.png}
+  \caption{The implementation structure of my framework.}\label{fig:outline}
 \end{figure}
@@
 \end{figure}
+
 This interface describes the necessary functions of a student strategy for the auctions exercise.
@@
 
-Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thereby rewritten to instantiate one implementation of each Student class listed in the configuration file:
+Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the method in Figure~\ref{minted:oneEachTrial} will be rewritten to instantiate one object of each Student implementation listed in the configuration file:
 \begin{figure}[hbt]
@@
 \end{figure}
-
 My modular design allows for data collection code to vary without additional overhead.
-The following method instantiates an instance of an instructor-provided strategy using reflection, in addition to the strategies specified in the configuration file.
+This is shown in Figure~\ref{minted:withExtraTrial}, which instantiates an instructor-provided strategy using reflection, in addition to the strategies specified in the configuration file.
 This method is useful for grading assignments.
@@
 
-In summary, as described in Figuree~\ref{figure:outline}, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.
+In summary, as described in Figure~\ref{fig:outline}, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.
 
@@
 
-% Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.
-
 % What are your thoughts on how well the strategy design exercises have gone this year?
 Specifically, I'm interested in your satisfaction with the implementations and software, and the amount of instructor time and frustration spent.
-(And less intersted in comments on the course policy decisions that may have impacted how well they went, sicne that's not in the scope of my independent work.)
 
@@
 This paper represents my own work in accordance with university regulations.
+
+\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
+\medskip
+\printbibliography[]
 

### 2018-05-07 paper.tex
BibLaTeX

@@
 Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
-Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}~\cite{coursesizes}
+Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton~\cite{coursesizes}.\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}
 
@@
 For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
-The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.~\cite{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
+The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems~\cite{cos445sp18}.
 It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
@@
 Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
-A classic iterated game is the iterated prisoner's dilemma,\footnote{Figure: PD game -> Java interface} in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
+A classic iterated game is the iterated prisoner's dilemma, as in Figure~\ref{fig:pd},
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[scale=0.5]{pd.png}
+  \caption{The payoffs of each round of the iterated prisoner's dilemma.}\label{fig:pd}
+\end{figure}
+in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
 Players balance the incentive to defect, which improves their own situation while damaging their opponent, with the knowledge that their opponent may defect in future rounds punish them if they defect now.
+This game translates to the interface in Figure~\ref{minted:Prisoner}.
+\begin{figure}[hbt]
+\begin{minted}{java}
+    public static <Student_T extends Student> int[] withExtraTrial(
+            Class<Student_T> clazz, double S, double T, double W)
+    {
+        // Initialize students
+        Student[] students = new Student[N+1];
+        //R students[{0}] = new Student_{netID}();//
+        try {
+            students[N] = clazz.getConstructor().newInstance();
+        } catch (ReflectiveOperationException roe) {
+            roe.printStackTrace();
+            System.exit(1);
+        }
+
+        return runTrial(students, S, T, W);
+    }
+\end{minted}
+  \caption{\texttt{interface Prisoner} demonstrates a strategy interface}\label{minted:Prisoner}
+\end{figure}
 While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
@@
 
-While the strategy design exercises assignments are popular with students~\cite{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
+While the strategy design exercises assignments are popular with students~\cite{cos445sp17review}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
 Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
@@
 \section*{Related Work}
-This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.~\cite{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
+This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017~\cite{cos445sp17}.
 In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different abstract games: Prisoner's Dilemma, Centipede, and Ultimatum.
@@
 
-Both problem sets were implemented and graded by Cyril Zhang~\cite{https://github.com/cyrilzhang}, a graduate student TA for the course.
-Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
+Both problem sets were implemented and graded by Cyril Zhang~\cite{cyrilzhang}, a graduate student TA for the course.
+Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise~\cite{s17}.
 However, his implementation of software for strategy design assignments was intended for grader use only.
@@
 
-Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014~\cite{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
+Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014~\cite{coursehistory}.
 Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
-In both semesters, Yonatan Naamad,~\cite{https://github.com/ynaamad/} a former graduate student TA for the course, was responsible for software development.
+In both semesters, Yonatan Naamad~\cite{ynaamad}, a former graduate student TA for the course, was responsible for software development.
 
-The only resources available from Fall 2012 were collected from the course Google Code repository.~\cite{https://code.google.com/archive/p/cos445-scripts/}
+The only resources available from Fall 2012 were collected from the course Google Code repository~\cite{googlecode}.
 This repository contains incomplete Python skeleton code for a basic tournament of an unspecified game.
-I uploaded this code to the current course repository~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.
+I uploaded this code to the current course repository~\cite{f12} but did not develop it further.
 
-The Spring 2014 iteration of the course was developed on a private GitHub repository.~\cite{https://github.com/ynaamad/cos445}
+The Spring 2014 iteration of the course was developed on a private GitHub repository at ynaamad:cos445, which I am unable to access directly.
 Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
@@
 As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
-These resources were uploaded to the current course repository,~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.
+These resources were uploaded to the current course repository~\cite{s14}, but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.
 
 Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
-However, a survey of several universities' courses, including courses at Harvard~\cite{https://beta.blogs.harvard.edu/k108875/}, Stanford~\cite{https://theory.stanford.edu/~tim/364a.html}~\cite{https://theory.stanford.edu/~tim/f16/f16.html}, Cornell~\cite{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington~\cite{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale~\cite{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn~\cite{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech~\cite{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon~\cite{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke~\cite{https://www2.cs.duke.edu/courses/spring16/compsci590.4/}, identified only one other course with similarly-structured assignments.
+However, a survey of several universities' courses, including courses at Harvard~\cite{harvard}, Stanford~\cite{stanford364a}~\cite{stanfordf16}, Cornell~\cite{cornell}, U.\ Washington~\cite{uw}, Yale~\cite{yale}, U.\ Penn~\cite{penn}, Georgia Tech~\cite{gtech}, MIT~\cite{mit}, Carnegie Mellon~\cite{cmu}, and Duke~\cite{duke}, identified only one other course with similarly-structured assignments.
 
-Harvard's Computer Science 136, ``Economics and Computation''~\cite{https://beta.blogs.harvard.edu/k108875/assignments/}, assigns two programming problem sets.
+Harvard's Computer Science 136, ``Economics and Computation''~\cite{harvard}, assigns two programming problem sets.
 The first requires implementation of a peer-to-peer file sharing system similar to BitTorrent, a protocol in which incentives parallel Prisoner's Dilemma.
@@
 Though existing automatic grading systems cannot replicate the full extent of this work, I have integrated existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
-I integrated CS DropBox~\cite{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
+I integrated CS DropBox~\cite{csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
 Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.
@@
 
-Many students suggested the assignments be implemented in Python,~\cite{per survey 1 results} and this would be preferred by the course staff as well.
+Many students suggested the assignments be implemented in Python,\footnote{TODO: per survey 1 results} and this would be preferred by the course staff as well.
 Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
@@
 Unfortunately, COS 445's prerequisite courses only provide Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
-Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.~\cite{COS 333 survey data}
+Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{TODO: COS 333 survey data}
 Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
@@
 This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and non-null unless otherwise explicitly specified.
-Current industry standards for Java code obviate both of these issues using modern language features.~\cite{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}~\cite{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}~\cite{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
+Current industry standards for Java code obviate both of these issues using modern language features~\cite{guavanull, guavaimmutable, unmodlist}.
 In order to preserve backwards compatibility, these features are not implemented by default.
@@
 However, I have not included \texttt{NotNull} annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
-In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.~\cite{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}
+In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016~\cite{techworld}, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.
 
@@
 The game simulates college admissions using stable matchings.
-While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.~\cite{Kernighan and Pike chapter 4}
+While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217~\cite[Chapter~4]{tpop99}.
 I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.
@@
 This project has already achieved minimum viable product by providing a framework for implementation of strategy design exercises in the current year of COS 445.
-These assignments and the framework I developed are documented and available at the course GitHub site.~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s18 requires invite}
+These assignments and the framework I developed are documented and available at the course GitHub site~\cite{s18}.
 Thus, they will be available for reuse in future offerings of the course.
@@
 \item empirical results about student error rates
-  ``Illegal submissions'' constitute student strategies which do not compile, throw exceptions, violate assertions, or otherwise behave outside of the parameters of the simulation.~\cite{Poorly performing strategies which obey the specification are legal.}
+  ``Illegal submissions'' constitute student strategies which do not compile, throw exceptions, violate assertions, or otherwise behave outside of the parameters of the simulation.\footnote{Poorly performing strategies which obey the specification are legal.}
   The illegal submission rate measures the percentage of students who were unable to develop a quality strategy for reasons other than lack of mastery of the course content.
@@
 Recently, I became aware of a Java interface for loading classes at run time.
-This technology, called ClassLoader,~\cite{https://docs.oracle.com/javase/9/docs/api/java/lang/ClassLoader.html} was implemented in the Spring 2014 handout code.
+This technology, called ClassLoader~\cite{classloader}, was implemented in the Spring 2014 handout code.
 I was unable to use ClassLoaders initially because I did not gain access to the Spring 2014 code until later in the semester.
@@
 
-\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
 \medskip
+\singlespacing{}
 \printbibliography[]
@@
 \begin{appendices}
-  \singlespacing{}
   \appendixpage{}

### 2018-05-07 paper.tex
Almost done results!

@@
 \usepackage{titling}
+
+\usepackage{fancyvrb}
 
@@
 
-Many students suggested the assignments be implemented in Python,\footnote{TODO: per survey 1 results} and this would be preferred by the course staff as well.
+Many students suggested the assignments be implemented in Python~\cite{survey12, survey34}, and this would be preferred by the course staff as well.
 Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
@@
 Unfortunately, COS 445's prerequisite courses only provide Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
-Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{TODO: COS 333 survey data}
+Data from other course surveys (Appendix~\ref{appendix:cos333sp17}, Appendix~\ref{appendix:cos333sp18}) indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.
 Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
@@
 While I have been unable to experimentally determine whether my project will be reused, I have evaluated my successful achievement of each other goal.
-I have decreased the work to build each assignment within a semester and the instructor time allocated to assignment implementation, eliminated the inter-year assignment reconstruction, and improved available student resources
+I have decreased the work to build each assignment within a semester and the instructor time allocated to assignment implementation, eliminated the inter-year assignment reconstruction, and improved available student resources.
 These achievements have increased student and instructor satisfaction with the strategy design exercises.
@@
 My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment-to-assignment rewriting.
-\begin{itemize}
-\item code rewriting measurements between assignments
-\item instructor time usage
-\item extensibility:
-\end{itemize}
+As measured using \texttt{cloc}, development of the fourth strategy design exercise required only TODO\% of the code be modified from previous assignments~\cite{s18}.\footnote{TODO lines of code be changed out of TODO lines of code total assigned or graded.}
+As illustrated in Figure~\ref{fig:instructortime}, which shows each assignment from Spring 2018 in chronological order, instructor time usage dropped radically with each exercise, demonstrating the benefits of modular design.\footnote{This data is exaggerated by the overhead of modularization and includes time spent on framework development where that was a direct dependency of instructor work.}
+
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.75\linewidth]{instructortime.png}
+  \caption{Instructor time usage dropped radically as my framework was deployed. (Table~\ref{table:time})}\label{fig:instructortime}
+\end{figure}
 
 I have also succeeded at leveraging the extensibility of my project to improve student resources.
-
-\begin{itemize}
-\item list resources created
-\item polling data about student usage
-\item empirical results about student error rates
+As measured using \texttt{cloc}, the ``Check Submit'' button required 28 lines of code and the leaderboard required 34 lines of code to implement~\cite{s18}, representing roughly 15\% each of the size framework developed previously.
+With these remarkably simple extensions, student performance improved dramatically.
 ``Illegal submissions'' constitute student strategies which do not compile, throw exceptions, violate assertions, or otherwise behave outside of the parameters of the simulation.\footnote{Poorly performing strategies which obey the specification are legal.}
 The illegal submission rate measures the percentage of students who were unable to develop a quality strategy for reasons other than lack of mastery of the course content.
-\end{itemize}
+As shown in Figure~\ref{fig:illegal}, the illegal submission rate dropped from over 20\% to just one or two strategies per assignment as the extensions I had developed were deployed.\footnote{The leaderboard and ``Check Submit'' button were first available for Ultimatum.}
+
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.75\linewidth]{illegal.png}
+  \caption{Illegal submission rate dropped as my extensions were deployed. (Table~\ref{table:illegal})}\label{fig:illegal}
+\end{figure}
+
+Student polling data gathered at multiple points during the semester confirms that student engagement with newly released tools coincided with decreased rates of illegal submissions.
+After the first two strategy design exercises, during which only the handout was provided, 68 of 74 respondents (out of 142 enrolled students) reported having used the handout to test their strategies~\cite{survey12}.
+TODO student usage 34
 
@@
 In addition to the data gathered above, I verified this achievement by surveying the current students of COS 445 under the supervision of Professor Weinberg.
-\begin{itemize}
-\item polling data about student usage
-\end{itemize}
+In addition to usage data referenced above, survey respondents also evaluated their subjective rating for how useful the provided framework was in the design of their strategies.
+TODO student rating 12 34
 
-% What are your thoughts on how well the strategy design exercises have gone this year?
+In order to evaluate instructor experiences, I reached out to Professor Weinberg for comment:
+\begin{displayquote}
+Andrew: What are your thoughts on how well the strategy design exercises have gone this year?
 Specifically, I'm interested in your satisfaction with the implementations and software, and the amount of instructor time and frustration spent.
 
-% ** significantly** improved instructor involvement.
-% I didn't actually touch any of the software directly, so I don't know how to comment on that.
+Professor Weinberg: We have \textbf{significantly} improved instructor involvement.
+I didn't actually touch any of the software directly, so I don't know how to comment on that.
 But I felt like the challenges mostly ran themselves.
 We talked briefly to set it up.
-We talked briefly to decide how to grade, and I didn't have to answer any technical questions for students in between
+We talked briefly to decide how to grade, and I didn't have to answer any technical questions for students in between.
+\end{displayquote}
+My own experience an undergraduate course assistant using the framework I have developed in this work corroborates this claim: this project has led to better course experiences for all involved.
 
@@
   \section{\texttt{students.csv} provides an example configuration for \texttt{formatBase.py}}\label{appendix:students}
-\begin{verbatim}
+\begin{Verbatim}
 netID
@@
 favorites
-\end{verbatim}
+\end{Verbatim}
+
+\newpage
+\section{COS 333 Spring 2017 Survey Data}\label{appendix:cos333sp17}
+Thanks to Professor Kernighan for providing my independent work seminar with this data.
+\begin{Verbatim}[fontsize=\scriptsize]
+181 responses
+Class
+ 2017 10
+ 2018 89
+ 2019 82
+Major
+ COS 148        ELE 12         ORF 4          WWS 2          MAT 2          ECO 2         
+ SPA 1          POL 1          PHI 1          HIS 1          GER 1          AST 1         
+ ARC 1          AB 1           A.B. 1        
+Certificate  23
+Course
+ C217 178       C226 175       C126 161       C326 36        C318 21        C461 8        
+ C418 1         C320 1        
+Fluent
+ Java 133       C 61           Python 32      Javascript 17  HTML 9         OCaml 6       
+ Matlab 6       R 5            Swift 4        English 4      CSS 4          C++ 4         
+ C# 4           PHP 3          Verilog 2      Ruby 2         Assembly 2     X86-64 1      
+ TypeScript 1   Scala 1        SQL 1          SCSS 1         Perl 1         Ofcourse 1    
+ NodeJavascrip  Haskell 1      Greek 1        ChucK 1       
+Cope:
+ Python 41      C 37           HTML 24        Javascript 17  Java 15        CSS 13        
+ OCaml 12       Matlab 10      C++ 10         PHP 9          Ruby 8         C# 8          
+ Swift 7        Verilog 6      SQL 6          R 6            MySQL 3        Assembly 3    
+ x86-64 2       VB 2           Rails 2        Perl 2         Go 2           Fortran 2     
+ 3 1            x86 1          up 1           seem 1         regular 1      only 1        
+ not 1          most 1         mark 1         little 1       learn 1        languages 1   
+ iOS-Swift 1    extremely 1    but 1          bit 1          X86 1          WebGL 1       
+ VBA 1          Scheme 1       SCSS 1         Rust 1         React-Native   React 1       
+ OpenGL 1       Objective 1    N 1            Lisp 1         LaTeX 1        I 1           
+ Haskell 1      Common 1       Coffeescript   Clojure 1      Can 1          Bash 1        
+ Arabic 1       Android 1      AVR 1          AMPL 1         - 1           
+More:
+ Python 42      Javascript 33  Ruby 23        C++ 22         Swift 20       SQL 17        
+ PHP 17         HTML 16        Go 14          CSS 9          Perl 5         Haskell 5     
+ C# 5           C 5            Scala 4        iOS 3          Rust 3         Objective 3   
+ OCaml 3        languages 2    functional 2   else 2         anything 2     React 2       
+ MySQL 2        Lisp 2         Erlang 2       Clojure 2      Android 2      what's 1      
+ web 1          to 1           them 1         or 1           often 1        of 1          
+ mobile 1       maybe 1        lot 1          language? 1    know 1         jQuery 1      
+ in 1           front-end 1    for 1          everything 1   especially 1   emacs 1       
+ else. 1        don't 1        dev 1          css 1          app 1          Super 1       
+ Solidity 1     Scripts 1      R 1            Prolog 1       Or 1           Open 1        
+ Objective-C 1  Not 1          NodeJavascrip  Mongo 1        Mobile 1       Maybe 1       
+ Matlab 1       Lua 1          Julia 1        JQuery 1       Idris 1        IOS 1         
+ I 1            FORTRAN 1      F# 1           Everything 1   Dev 1          D 1           
+ Coq 1          CoffeeScript   Chinese 1      Arabic 1       App 1          Any 1         
+ All 1          .NET 1        
+Unix      48  37  59  34
+Win       86  35  40  16
+Mac       78  25  45  30
+iOS      126  25  21   5
+Android  107  40  25   7
+Win 55, Mac 134, Linux 12
+iPhone 126, Android 55, Other 0
+181 responses
+\end{Verbatim}
+
+\newpage
+\section{COS 333 Spring 2018 Survey Data}\label{appendix:cos333sp18}
+Thanks to Professor Kernighan for providing my independent work seminar with this data.
+\begin{Verbatim}[fontsize=\scriptsize]
+Names 103
+2018 14
+2019 25
+2020 64
+ 103
+Majors:
+   cos 82
+   ele 6
+   orf 5
+   phy 2
+   mae 2
+   eco 2
+   mol 1
+   mat 1
+   geo 1
+   ast 1
+Certif 17
+126 93
+217 100
+226 102
+318 2
+320 
+326 11
+418 3
+425 
+435 1
+436 
+461 12
+Unix    lots 13 some 55 little 22 none 12
+Win lots 19 some 32 little 16 none 33
+MacOSX  lots 20 some 29 little 14 none 39
+iOS lots 7 some 11 little 16 none 67
+Android lots 8 some 14 little 24 none 54
+PCwin 42
+PClinux 9
+PCmac 66
+iPhone 64
+Android 40
+other 0
+Fluent
+   java 91 c 67 python 29 javascript 8 c++ 8 r 7 matlab 6 html 6 ocaml 4
+   css 4 react 3 swift 2 asm 2 wolfram 1 verilog 1 stata 1 sql 1 scala 1
+   ruby 1 php 1 objective-c 1 native 1 latex 1 julia 1 jquery 1 fortran 1
+   bash 1
+Cope
+   python 35 c 30 javascript 21 r 12 c++ 12 java 11 matlab 9 html 9 sql 6
+   ocaml 6 php 5 css 5 swift 4 go 3 asm 3 verilog 2 ruby 2 objective-c 2
+   lua 2 c# 2 xml 1 throwback 1 stata 1 scala 1 roughly 1 rails 1 other 1
+   mysql 1 know 1 julia 1 i 1 haskell 1 fortran 1 f# 1 c#.net 1 at&t 1
+   ample 1 VB 1 64 1
+More
+   javascript 38 python 37 c++ 22 html 17 sql 14 ruby 11 go 11 swift 8
+   css 8 c# 7 scala 5 react 3 perl 3 haskell 3 web 2 php 2 other 2 c 2
+   them 1 stack 1 rust 1 reactjavascript 1 rails 1 r 1 others 1 of 1
+   ocaml 1 objective-c 1 native 1 mysql 1 my 1 missing 1 mean 1 matlab 1
+   many 1 list 1 latex 1 languages 1 kotlin 1 java 1 is 1 ios 1 http 1
+   html5 1 hadoop 1 golang 1 git 1 from 1 frameworks 1 experience 1
+   everything 1 etc.  1 essential 1 else 1 databases 1 clojure 1 awk 1
+   application 1 android 1
+\end{Verbatim}
+
+\newpage
+\section{Data Tables}\label{appendix:tables}
+
+\begin{table}[!h]
+  \centering
+  \begin{tabular}{l|c c c}  & Design& Build& Grade\\
+    \hline
+    1. Matching& 5& 15& 20\\
+    2. Election& 5& 10& 15\\
+    3. Ultimatum& 5& 5& 5\\
+    4. Auction& 5& 1.5& 5
+  \end{tabular}
+  \caption{Instructor time usage per assignment (hours)}\label{table:time}
+\end{table}
+This data is approximate and based on revision logs reviewed later in the semester.
+Instructor time usage for early assignments includes framework development not performed by course staff where that work was necessary for the completion of the assignment development and grading.
+
+\begin{table}[!h]
+  \centering
+  \begin{tabular}{l|c c c} & Compile Error& Runtime Error& None\\
+    \hline
+    1. Matchings& 9& 12& 61\\
+    2. Elections& 4& 6& 70\\
+    3. Ultimatum& 2& 0& 75\\
+    4. Auction& 0& 1& 75
+  \end{tabular}
+  \caption{Incidence of illegal submissions per assignment}\label{table:illegal}
+\end{table}
+I accessed this data in my role as an undergraduate course assistant and received Professor Weinberg's approval to include it in this paper.
+
 \end{appendices}

### 2018-05-07 paper.tex
Finished results! Draft complete

@@
 My primary goal, which unifies my work and sets it apart from past work on this subject, has been to discover modularity and decrease assignment-to-assignment rewriting.
-As measured using \texttt{cloc}, development of the fourth strategy design exercise required only TODO\% of the code be modified from previous assignments~\cite{s18}.\footnote{TODO lines of code be changed out of TODO lines of code total assigned or graded.}
+As measured using \texttt{cloc}, development of the fourth strategy design exercise required only 33\% of the code be modified from previous assignments~\cite{s18}.\footnote{69 lines of code were changed out of 208 lines of code total in the development of the auctions assignment.
+This data also demonstrates how the assignment handouts are fairly succinct.}
 As illustrated in Figure~\ref{fig:instructortime}, which shows each assignment from Spring 2018 in chronological order, instructor time usage dropped radically with each exercise, demonstrating the benefits of modular design.\footnote{This data is exaggerated by the overhead of modularization and includes time spent on framework development where that was a direct dependency of instructor work.}
@@
   \includegraphics[width=0.75\linewidth]{illegal.png}
-  \caption{Illegal submission rate dropped as my extensions were deployed. (Table~\ref{table:illegal})}\label{fig:illegal}
+  \caption{Illegal submission rate dropped as my extensions were deployed (Table~\ref{table:illegal}).}\label{fig:illegal}
 \end{figure}
@@
 After the first two strategy design exercises, during which only the handout was provided, 68 of 74 respondents (out of 142 enrolled students) reported having used the handout to test their strategies~\cite{survey12}.
-TODO student usage 34
+At the end of the course, students were asked to give feedback on changes in strategy design write-up grading.
+As a part of that survey, students were asked: which of the resources developed as a part of this work they used in the process of developing their strategies?
+Of the 142 enrolled students, there were 31 survey respondents, and 29 of the survey respondents used some of the provided infrastructure.
+As shown in Figure~\ref{fig:usage2}, most students made usage of some of the additional resources.
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.75\linewidth]{usage2.png}
+  \caption{Students used the additional resources provided with Ultimatum and Auction~\cite{survey34}.}\label{fig:usage2}
+\end{figure}
+Individual responses show an even higher rate of usage than this data suggests: 24 of the 31 respondents used either the ``Check Submit'' button or the leaderboard to test a strategy.
 
-Through this work, I have improved student and instructor experiences.
-In addition to the data gathered above, I verified this achievement by surveying the current students of COS 445 under the supervision of Professor Weinberg.
+Through the development of these tools, I have improved student and instructor experiences.
+I verified this achievement by surveying the current students of COS 445 under the supervision of Professor Weinberg.
 In addition to usage data referenced above, survey respondents also evaluated their subjective rating for how useful the provided framework was in the design of their strategies.
-TODO student rating 12 34
+Initial responses shown in Figure~\ref{fig:useful1} to the fully functioning simulation software developed using my framework were positive.
+This ``testing infrastructure'' was provided in the handout for the first two software design exercises.
+As noted previously, even this handout provided more advanced functionality than had been available to students in previous offerings of COS 445.
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.75\linewidth]{useful1.png}
+  \caption{Students found the handout provided with Matchings and Elections useful~\cite{survey12}.}\label{fig:useful1}
+\end{figure}
+
+After the deployment of the ``Check Submit'' button and leaderboard, students had access to three different evaluation criteria for their strategies.
+Figure~\ref{fig:useful2} demonstrates that students later in the semester positively evaluated all three tools, and that students had become more supportive over time of the ability to test many different strategies on their own computers.
+This suggests an alternate interpretation of the decrease in illegal submissions: not just is it important to provide quality tooling to students, but also it is important for the students to use those tools.
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.75\linewidth]{useful2.png}
+  \caption{Students found the additional resources provided with Ultimatum and Auction useful~\cite{survey34}.}\label{fig:useful2}
+\end{figure}
 

### 2018-05-08 paper.tex
Turned it in!

@@
 This data also demonstrates how the assignment handouts are fairly succinct.}
-As illustrated in Figure~\ref{fig:instructortime}, which shows each assignment from Spring 2018 in chronological order, instructor time usage dropped radically with each exercise, demonstrating the benefits of modular design.\footnote{This data is exaggerated by the overhead of modularization and includes time spent on framework development where that was a direct dependency of instructor work.}
-
+As illustrated in Figure~\ref{fig:instructortime}, which shows each assignment from Spring 2018 in chronological order, instructor time spent building and grading assignments dropped radically with each exercise, demonstrating the benefits of modular design.\footnote{This data is exaggerated by the overhead of modularization and includes time spent on framework development where that was a direct dependency of instructor work.}
+Improving the efficiency of the assignment design process was not within the scope of this work.
 \begin{figure}[hbt]
@@
   \includegraphics[width=0.75\linewidth]{instructortime.png}
-  \caption{Instructor time usage dropped radically as my framework was deployed. (Table~\ref{table:time})}\label{fig:instructortime}
+  \caption{Instructor time usage dropped radically as my framework was deployed (Table~\ref{table:time}).}\label{fig:instructortime}
 \end{figure}
@@
 Student polling data gathered at multiple points during the semester confirms that student engagement with newly released tools coincided with decreased rates of illegal submissions.
-After the first two strategy design exercises, during which only the handout was provided, 68 of 74 respondents (out of 142 enrolled students) reported having used the handout to test their strategies~\cite{survey12}.
+The first poll was taken after the first two strategy design exercises, during which only the handout was provided.
+Out of 142 enrolled students, there were 74 survey responses, of which 68 reported having used the handout to test their strategies~\cite{survey12}.
 At the end of the course, students were asked to give feedback on changes in strategy design write-up grading.
-As a part of that survey, students were asked: which of the resources developed as a part of this work they used in the process of developing their strategies?
-Of the 142 enrolled students, there were 31 survey respondents, and 29 of the survey respondents used some of the provided infrastructure.
+As a part of that survey, students were asked which of the resources developed as a part of this work they used in the process of developing their strategies.
+There were 31 responses to the second survey and 29 of these reported use of some of the provided infrastructure.
 As shown in Figure~\ref{fig:usage2}, most students made usage of some of the additional resources.
@@
   \caption{Students used the additional resources provided with Ultimatum and Auction~\cite{survey34}.}\label{fig:usage2}
+  \caption*{Percentages include only students who reported using any provided resource.}
 \end{figure}
@@
   \caption{Students found the handout provided with Matchings and Elections useful~\cite{survey12}.}\label{fig:useful1}
+  \caption*{Scores were given from 1 (not useful) to 5 (useful).}
 \end{figure}
@@
 Figure~\ref{fig:useful2} demonstrates that students later in the semester positively evaluated all three tools, and that students had become more supportive over time of the ability to test many different strategies on their own computers.
-This suggests an alternate interpretation of the decrease in illegal submissions: not just is it important to provide quality tooling to students, but also it is important for the students to use those tools.
+This suggests an alternate interpretation of the decrease in illegal submissions: it is not just important to provide quality tooling to students, but also important that the students use those tools.
 \begin{figure}[hbt]
@@
 \end{displayquote}
-My own experience an undergraduate course assistant using the framework I have developed in this work corroborates this claim: this project has led to better course experiences for all involved.
+My own experience an undergraduate course assistant using the framework I have developed in this work corroborates the claim that this project has led to better course experiences for all involved.
 
